---
title: "FRANIG Seed Morphology - Aster Models"
author: "KyraL"
date: "2026-01-07"
output: html_document
---
#Introduction
The code here was used to construct Aster life history models and predict cumulative fitness for each population. Those fitness predictions were then used in linear regression to test if population climat of origin predicts seedlings fitness.

#Clean the full dataset
```{r}
#time to emergence, true leaves, and compound leaves was done in excel because dates are hard to work with
Aster_PhenologyData <- read_excel("FRANIGCG_2024_LifeHistoryRawData.xlsx")
Aster_HeightData <- read_excel("Fall2024_HeightData.xlsx")

#remove entries where no seed was planted
Aster_PhenologyData <- Aster_PhenologyData[Aster_PhenologyData$Emergence_Date_MMDDYY != "no seed" | is.na(Aster_PhenologyData$Emergence_Date_MMDDYY),]

#remove unnecessary columns
pheno_cleaned <- Aster_PhenologyData[,c(3:10,26:28)] #keep seed ID for now

#create a seed ID column in the height sheet
Aster_HeightData$Seed_ID <- paste(Aster_HeightData$Maternal_ID,Aster_HeightData$Seed_No, sep = "-")
#remove unnecessary columns
height_cleaned <- Aster_HeightData[,c(8,11)]


#merge data frames
df <- full_join(pheno_cleaned, height_cleaned, by = "Seed_ID")
df$`Height(cm)` <- as.numeric(df$`Height(cm)`)

#set entries where no seed emerged to have a time to emergence of 0
df$Time_to_Emergence[df$Time_to_Emergence < 0] <- 0

#remove individuals that have a height but do not have any emergence data
df <- df[!( (df$Time_to_Emergence == 0 | is.na(df$Time_to_Emergence)) &
             !is.na(df$`Height(cm)`) ), ]

#make a column for if the seed emerged or not
df$emerge01 <- ifelse(df$Time_to_Emergence <= 0 | is.na(df$Time_to_Emergence), 0,1)
df$Time_to_Emergence[is.na(df$Time_to_Emergence)] <- 0


#make a column for if the seedling produced true leaves or not
df$true01 <-  ifelse(df$Time_to_TrueLeaves <= 0 | is.na(df$Time_to_TrueLeaves), 0, 1)
#replace NA true leaf values with 0
df$Time_to_TrueLeaves[df$Time_to_TrueLeaves < 0] <- 0
df$Time_to_TrueLeaves[is.na(df$Time_to_TrueLeaves)] <- 0


#make column for if the seedling produced compound leaves or not
df$comp01 <-  ifelse(df$Time_to_CompoundLeaves <= 0 | is.na(df$Time_to_CompoundLeaves), 0, 1)
#replace NA compound leaf values with 0
df$Time_to_CompoundLeaves[df$Time_to_CompoundLeaves < 0] <- 0
df$Time_to_CompoundLeaves[is.na(df$Time_to_CompoundLeaves)] <- 0

#make a mortality column based on height data
df$mort01 <- ifelse(df$`Height(cm)` == 0 | is.na(df$`Height(cm)`), 0,1)
#make height measurements that are NA equal to 0
df$`Height(cm)`[is.na(df$`Height(cm)`)] <- 0

#remove twins
df <- df[grepl("^[0-9]+(\\.[0-9]+)?$", df$`Height(cm)`), ]

#remove the Seed_ID column
df <- df[,c(1,3:16)]

write.csv(df, file = "AsterFullDataset_Fall2025.csv")
```

#Put data in Aster format
```{r}
AsterTestData_Cleaned <- read_csv("AsterFullDataset_Fall2025.csv")
df <- AsterTestData_Cleaned[,-1]
sapply(df, class)
colnames(df)[colnames(df) == "Time_to_Emergence"] <- "emerge02"
colnames(df)[colnames(df) == "Time_to_TrueLeaves"] <- "true02"
colnames(df)[colnames(df) == "Time_to_CompoundLeaves"] <- "comp02"
colnames(df)[colnames(df) == "Height(cm)"] <- "height01"

df$Individual <- as.factor(df$Individual)
df$Provenance <- as.factor(df$Provenance)
df$Year_Collected <- as.factor(df$Year_Collected)
df$Table <- as.factor(df$Table)
df$Latitude <- as.integer(df$Latitude)
df$Longitude <- as.integer(df$Longitude)
df$Elevation <- as.integer(df$Elevation)
df$emerge01 <- as.integer(df$emerge01)
df$emerge02 <- as.integer(df$emerge02)
df$true01 <- as.integer(df$true01)
df$true02 <- as.integer(df$true02)
df$comp01 <- as.integer(df$comp01)
df$comp02 <- as.integer(df$comp02)
df$mort01 <- as.integer(df$mort01)

sapply(df, class)

#remove individuals that have true leaves or compound leaves but no emergence data
df <- df[!(df$emerge01 == 0 & df$true01 == 1), ]
df <- df[!(df$emerge01 == 0 & df$comp01 == 1), ]
```

```{r}
#transform the data to long format
vars <- c("emerge01", "emerge02", "true01", "true02", 
          "comp01", "comp02", "mort01", "height01")

df <- as.data.frame(df)

redata <- reshape(df, varying = list(vars), direction = "long",timevar = "varb", times = as.factor(vars), v.names = "resp")

```

##add the root node, assign family distributions to each node, and assign predicessors
```{r}
library(aster)

redata <- data.frame(redata, root = 1)
names(redata)
famlist <- list(
  fam.bernoulli(),
  fam.truncated.poisson(0),
  fam.normal.location(sd =1)
)

fam <- c(1, 2, 1, 2, 1, 2, 1, 3)

pred <- c(0,1,1,3,3,5,1,7)

sapply(famlist, as.character)[fam]

fit <- grep("height01", as.character(redata$varb))
fit <- is.element(seq(along = redata$varb), fit)
redata <- data.frame(redata, fit = as.integer(fit))
names(redata)

```

#build aster model
Reaster models take a vary long time to run, so make sure you save the output as an R object
```{r}
aout3 <- reaster(resp ~ varb + fit:(Provenance + Seed_Weight+emerge02+true02+true01+comp02+comp01), list(fam = ~ 0 + fit:Individual),  pred, fam, varb, id, root, famlist=famlist, data=redata)
summary(aout3, show.graph = T)
saveRDS(aout3, file = "FullAsterModel.R")
```

#predict fitness from aster model
Code adapted from Kulbaba et al 2019
```{r}
#extract the main aster object from the model
aout <- aout3$obj
#number of nodes and individuals in the data
nnode <- ncol(aout$x)
nind <- nrow(aout$x)
#extract fixed and random effects
fixed <- aout3$fixed
random <- aout3$random
#get column names of all random effects
randlab <- unlist(lapply(aout3$random, colnames))
#identify which random effects are associated with individual (family)
include.random <- grepl("Individual", randlab, fixed = TRUE)
#create a copy of the output for manilupation
fake.out <- aout
#combined fixed and random effects into a single vector
fake.beta <- with(aout3, c(alpha, b[include.random]))
#combine all random effects into a single matrix
modmat.random <- Reduce(cbind, random)
#sanity check, ensure the number of column mathces the length of random coefficients
stopifnot(ncol(modmat.random) == length(aout3$b))
#Keep only columns corresponding to individuals, never forget drop = FALSE in programming R
modmat.random <- modmat.random[ , include.random, drop = FALSE]
#combined fixed effect matrix with filtered random effects matrix
fake.modmat <- cbind(fixed, modmat.random)


# now have to deal with objects of class aster (as opposed to reaster)
#ensure model amtrices are compatible with Aster's expected 3-way array structure
stopifnot(prod(dim(aout$modmat)[1:2]) == nrow(fake.modmat))
fake.modmat <- array(as.vector(fake.modmat),dim = c(dim(aout$modmat)[1:2], ncol(fake.modmat)))

#replace modmat with our constructed model matrix
fake.out$modmat <- fake.modmat

#total number of parameters
nparm <- length(aout3$alpha) + length(aout3$b) + length(aout3$nu)

#identify indices for fixed (alpha), random (b), and other parameters (nu)
is.alpha <- 1:nparm %in% seq_along(aout3$alpha)
is.bee <- 1:nparm %in% (length(aout3$alpha) + seq_along(aout3$b))
is.nu <- (! (is.alpha | is.bee))

# Extract the family matrix from random effects
m <- aout3$random$fam
View(m)

# Get the column names of the family matrix (individual identifiers)
individuals <- colnames(m)
idx <- match(individuals, colnames(m))

# Remove "fit:Individual" prefix to get family codes
fams <- colnames(m)[idx] |> sub("^fit:Individual", "", x = _)

# Subset the family matrix to the relevant individuals
m.fams <- m[, individuals, drop = F]

# Reshape to 3D array (individuals x nodes x families)
m.fams <- array(m.fams, c(nind, nnode, ncol(m.fams)))

# Keep only the last node for each individual
m.fams <- m.fams[, nnode,]

# Sanity checks: family matrix should contain only 0/1 indicators and exactly one per individual
stopifnot(as.vector(m.fams) %in% c(0, 1))
stopifnot(rowSums(m.fams) == 1)

# Convert individual names to integer codes
ind.codes <- as.integer(factor(individuals))

# Multiply family indicator matrix by individual codes to get family assignment
fams <- drop(m.fams %*% ind.codes)

# Unique family codes and index of first occurrence
sufams <- sort(unique(fams))
which.ind <- match(sufams, fams)

# Combine all parameters into a single vector
alphabeenu <- with(aout3, c(alpha, b, nu))

# Sanity checks on combined parameters
stopifnot(is.numeric(alphabeenu))
stopifnot(is.finite(alphabeenu))
stopifnot(length(alphabeenu) == nparm)

# Separate alpha, b, and nu parameters
alpha <- alphabeenu[is.alpha]
bee <- alphabeenu[is.bee]
nu <- alphabeenu[is.nu]

# Recreate fake.beta (for prediction) including only relevant random effects
fake.beta <- c(alpha, bee[include.random])
fake.out$coefficients <- fake.beta

# Make conditional predictions using the aster model
pout <- predict(fake.out, model.type = "conditional", is.always.parameter = TRUE)

# Convert predictions to a matrix with columns = nodes
xi <- matrix(pout, ncol = nnode)

# Compute overall expected fitness per individual (product across nodes)
mu <- apply(xi, 1, prod)

# Convert predictions to a data frame for convenience
xi <- as.data.frame(xi)

# Combine fitness values with family codes
familyfitness <- cbind(mu, fams)
colnames(familyfitness)[2] <- "Family_Code"

# Create a mapping of individual -> family
ind.factor <- factor(individuals)
familyfitness <- as.data.frame(familyfitness)
ind.codes <- as.integer(ind.factor)
fam_labels <- levels(ind.factor)
fam_key <- data.frame(Individual = individuals, Family_Code = ind.codes, Family_Label = fam_labels[ind.codes])

# Join family labels with fitness data
familyfitness <- left_join(familyfitness, fam_key, by = "Family_Code")

# Extract family names from factor labels
familyfitness$Family <- substr(familyfitness$Family_Label, 15,35)
familyfitness$Family <- as.factor(familyfitness$Family)

# Compute mean fitness per family
fam_means <- aggregate(mu ~ Family, data = familyfitness, FUN = mean)

# Extract provenance from family name
fam_means$Prov <- as.factor(substr(fam_means$Family, 11,13))

# Combine node-level predictions with family codes
famfitcomp <- cbind(xi, fams)
colnames(famfitcomp) <- c("Survival", "Height" ,"Family_Code")
famfitcomp <- as.data.frame(famfitcomp)

# Join family labels
famfitcomp <- left_join(famfitcomp, fam_key, by = "Family_Code")
famfitcomp$Family <- substr(famfitcomp$Family_Label, 15,35)
famfitcomp$Family <- as.factor(famfitcomp$Family)

# Compute mean Survival and Height per family
mort_means <- aggregate(Survival ~ Family, data = famfitcomp, FUN = mean)
height_means <- aggregate(Height ~ Family, data = famfitcomp, FUN = mean)

# Merge survival and height summaries
famfitcomp_means <- left_join(mort_means, height_means, by = "Family")

# Merge in overall family fitness (mu) values
famfitcomp_means <- left_join(famfitcomp_means, fam_means, by = "Family")

# Clean up redundant column and rename
famfitcomp_means <- famfitcomp_means[,-6]
colnames(famfitcomp_means)[4] <- "Prov"
write.csv(famfitcomp_means, file = "AsterPredictedFitness.csv")
```

#Linear regressions
```{r}
#load in data
AsterPredictedFitness <- read_csv("~/GitHub/Ash/FRANIG_Seed/Aster/AsterPredictedFitness.csv")

#calculate average fitness values per provenance
mean_survival <- aggregate(Survival ~ Prov, data = AsterPredictedFitness, FUN = mean)
mean_height <- aggregate(Height ~ Prov, data = AsterPredictedFitness, FUN = mean)
mean_mu <- aggregate(mu ~ Prov, data = AsterPredictedFitness, FUN = mean)
df_list <- list(mean_survival, mean_height, mean_mu)
fitness_populationmeans <- reduce(df_list, full_join, by = "Prov")

#load climate data
FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y <- read_csv("~/GitHub/Ash/FRANIG_Seed/FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y.csv")

colnames(FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y)[colnames(FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y) == "id2"] <- "Prov"
fitness_df <- left_join(fitness_populationmeans, FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y, by = "Prov")


#merge fitness and climate data
fitness_df <- left_join(fitness_populationmeans, FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y, by = "Prov")

```


```{r}
#cumulative fitness
library(gridExtra)
y_var <- "mu"
x_vars <- c("TD", "CMD", "DD5", "MAT","MSP","MAP","RH")

model_list <- list()
plot_list <- list()

for (x_var in x_vars) {
  
  # Fit the linear model
  formula <- as.formula(paste(y_var, "~", x_var))  # Create formula dynamically
  model <- lm(formula, data = fitness_df)
  
  model_list[[x_var]] <- model
  
  # Extract R² and p-value
  r2 <- summary(model)$r.squared
  p_value <- summary(model)$coefficients[2, 4]
  
   # Determine top-right position dynamically
  x_pos <- max(fitness_df[[x_var]], na.rm = TRUE) * 0.9  # Slightly left from max x
  y_pos <- max(fitness_df[[y_var]], na.rm = TRUE) * 0.9  # Slightly below max y
  
  # Generate ggplot
  p <- ggplot(fitness_df, aes_string(x = x_var, y = y_var)) +  # Use aes_string() for dynamic mapping
    geom_point() + 
    geom_smooth(method = "lm", se = T, color = "blue") +
    annotate("text", x = x_pos, y = y_pos,
             label = paste0("R² = ", round(r2, 3), "\nP = ", signif(p_value, 3)),
             size = 3, color = "black") + theme(panel.background = element_blank(), panel.grid.major =    element_line("grey")) +
    ggtitle(paste("mu", "vs", x_var)) + ylab("mu")
  
  # Print each plot
  plot_list[[x_var]] <- p
}
model_summary <- map_dfr(
  model_list,
  ~{
    sm <- summary(.x)
    coefs <- sm$coefficients
    
    tibble(
      R_squared = sm$r.squared,
      Estimate  = coefs[2, "Estimate"],
      Std_Error = coefs[2, "Std. Error"],
      P_value   = coefs[2, "Pr(>|t|)"]
    )
  },
  .id = "Predictor"
)
write.csv(model_summary, file = "aster_Climate_Mu_Stats_perPop.csv")

plots_combined <- marrangeGrob(grobs = plot_list, ncol = 2, nrow = 3)

ggsave("AsterRegressions_mu_perPop.pdf", plots_combined, width = 10, height = 7)


# Create a list to store diagnostic plots
diagnostic_plots <- list()

# Loop through each model in model_list
for (x_var in names(model_list)) {
  
  model <- model_list[[x_var]]
  resid <- residuals(model)
  fitted <- fitted(model)
  
  # --- QQ Plot of residuals ---
  qq_data <- data.frame(
    Theoretical = qqnorm(resid, plot.it = FALSE)$x,
    Sample = qqnorm(resid, plot.it = FALSE)$y
  )
  
  # Compute slope and intercept for qqline (like base R qqline)
  q_theoretical <- quantile(qq_data$Theoretical, probs = c(0.25, 0.75))
  q_sample <- quantile(qq_data$Sample, probs = c(0.25, 0.75))
  slope <- diff(q_sample) / diff(q_theoretical)
  intercept <- q_sample[1] - slope * q_theoretical[1]
  
  # --- QQ Plot with QQ Line ---
  qq_plot <- ggplot(qq_data, aes(x = Theoretical, y = Sample)) +
    geom_point() +
    geom_abline(slope = slope, intercept = intercept, color = "red", linetype = "dashed", linewidth = 0.8) +
    ggtitle(paste("QQ Plot of Residuals for", x_var)) +
    theme_bw()
  
  # --- Residuals vs Fitted Plot ---
  resid_plot <- ggplot(data.frame(Fitted = fitted, Residuals = resid),
                       aes(x = Fitted, y = Residuals)) +
    geom_point() +
    geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
    ggtitle(paste("Residuals vs Fitted for", x_var)) +
    xlab("Fitted Values") +
    ylab("Residuals") +
    theme_bw()
  
  # Combine both plots vertically
  combined_plot <- gridExtra::grid.arrange(qq_plot, resid_plot, ncol = 1)
  
  diagnostic_plots[[x_var]] <- combined_plot
}

# Save all diagnostic plots to a single PDF

plots_combined <- marrangeGrob(grobs = diagnostic_plots, ncol = 2, nrow = 2)

ggsave("AsterRegressions_Mu_diagnostic_perPop.pdf", plots_combined, width = 10, height = 7)


#height
y_var <- "Height"
x_vars <- c("TD", "CMD", "DD5", "MAT","MSP","MAP","RH")

model_list <- list()
plot_list <- list()

for (x_var in x_vars) {
  
  # Fit the linear model
  formula <- as.formula(paste(y_var, "~", x_var))  # Create formula dynamically
  model <- lm(formula, data = fitness_df)
  
  model_list[[x_var]] <- model
  
  # Extract R² and p-value
  r2 <- summary(model)$r.squared
  p_value <- summary(model)$coefficients[2, 4]
  
   # Determine top-right position dynamically
  x_pos <- max(fitness_df[[x_var]], na.rm = TRUE) * 0.9  # Slightly left from max x
  y_pos <- max(fitness_df[[y_var]], na.rm = TRUE) * 0.9  # Slightly below max y
  
  # Generate ggplot
  p <- ggplot(fitness_df, aes_string(x = x_var, y = y_var)) +  # Use aes_string() for dynamic mapping
    geom_point() + 
    geom_smooth(method = "lm", se = T, color = "blue") +
    annotate("text", x = x_pos, y = y_pos,
             label = paste0("R² = ", round(r2, 3), "\nP = ", signif(p_value, 3)),
             size = 3, color = "black") + theme(panel.background = element_blank(), panel.grid.major =    element_line("grey")) +
    ggtitle(paste("Height", "vs", x_var)) + ylab("Height")
  
  # Print each plot
  plot_list[[x_var]] <- p
}

model_summary <- map_dfr(
  model_list,
  ~{
    sm <- summary(.x)
    coefs <- sm$coefficients
    
    tibble(
      R_squared = sm$r.squared,
      Estimate  = coefs[2, "Estimate"],
      Std_Error = coefs[2, "Std. Error"],
      P_value   = coefs[2, "Pr(>|t|)"]
    )
  },
  .id = "Predictor"
)
write.csv(model_summary, file = "aster_Climate_height_Stats_perPop.csv")

plots_combined <- marrangeGrob(grobs = plot_list, ncol = 2, nrow = 3)

ggsave("AsterRegressions_Height_perPop.pdf", plots_combined, width = 10, height = 7)


# Create a list to store diagnostic plots
diagnostic_plots <- list()

# Loop through each model in model_list
for (x_var in names(model_list)) {
  
  model <- model_list[[x_var]]
  resid <- residuals(model)
  fitted <- fitted(model)
  
  # --- QQ Plot of residuals ---
  qq_data <- data.frame(
    Theoretical = qqnorm(resid, plot.it = FALSE)$x,
    Sample = qqnorm(resid, plot.it = FALSE)$y
  )
  
  # Compute slope and intercept for qqline (like base R qqline)
  q_theoretical <- quantile(qq_data$Theoretical, probs = c(0.25, 0.75))
  q_sample <- quantile(qq_data$Sample, probs = c(0.25, 0.75))
  slope <- diff(q_sample) / diff(q_theoretical)
  intercept <- q_sample[1] - slope * q_theoretical[1]
  
  # --- QQ Plot with QQ Line ---
  qq_plot <- ggplot(qq_data, aes(x = Theoretical, y = Sample)) +
    geom_point() +
    geom_abline(slope = slope, intercept = intercept, color = "red", linetype = "dashed", linewidth = 0.8) +
    ggtitle(paste("QQ Plot of Residuals for", x_var)) +
    theme_bw()
  
  # --- Residuals vs Fitted Plot ---
  resid_plot <- ggplot(data.frame(Fitted = fitted, Residuals = resid),
                       aes(x = Fitted, y = Residuals)) +
    geom_point() +
    geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
    ggtitle(paste("Residuals vs Fitted for", x_var)) +
    xlab("Fitted Values") +
    ylab("Residuals") +
    theme_bw()
  
  # Combine both plots vertically
  combined_plot <- gridExtra::grid.arrange(qq_plot, resid_plot, ncol = 1)
  
  diagnostic_plots[[x_var]] <- combined_plot
}

# Save all diagnostic plots to a single PDF

plots_combined <- marrangeGrob(grobs = diagnostic_plots, ncol = 2, nrow = 2)

ggsave("AsterRegressions_Height_diagnostic_perPop.pdf", plots_combined, width = 10, height = 7)


#survival
y_var <- "Survival"
x_vars <- c("TD", "CMD", "DD5", "MAT","MSP","MAP","RH")

model_list <- list()
plot_list <- list()

for (x_var in x_vars) {
  
  # Fit the linear model
  formula <- as.formula(paste(y_var, "~", x_var))  # Create formula dynamically
  model <- lm(formula, data = fitness_df)
  
  model_list[[x_var]] <- model
  
  # Extract R² and p-value
  r2 <- summary(model)$r.squared
  p_value <- summary(model)$coefficients[2, 4]
  
   # Determine top-right position dynamically
  x_pos <- max(fitness_df[[x_var]], na.rm = TRUE) * 0.9  # Slightly left from max x
  y_pos <- max(fitness_df[[y_var]], na.rm = TRUE) * 0.9  # Slightly below max y
  
  # Generate ggplot
  p <- ggplot(fitness_df, aes_string(x = x_var, y = y_var)) +  # Use aes_string() for dynamic mapping
    geom_point() + 
    geom_smooth(method = "lm", se = T, color = "blue") +
    annotate("text", x = x_pos, y = y_pos,
             label = paste0("R² = ", round(r2, 3), "\nP = ", signif(p_value, 3)),
             size = 3, color = "black") + theme(panel.background = element_blank(), panel.grid.major =    element_line("grey")) +
    ggtitle(paste("Survival", "vs", x_var)) + ylab("Survival")
  
  # Print each plot
  plot_list[[x_var]] <- p
}

model_summary <- map_dfr(
  model_list,
  ~{
    sm <- summary(.x)
    coefs <- sm$coefficients
    
    tibble(
      R_squared = sm$r.squared,
      Estimate  = coefs[2, "Estimate"],
      Std_Error = coefs[2, "Std. Error"],
      P_value   = coefs[2, "Pr(>|t|)"]
    )
  },
  .id = "Predictor"
)
write.csv(model_summary, file = "aster_Climate_survival_Stats_perPop.csv")

plots_combined <- marrangeGrob(grobs = plot_list, ncol = 2, nrow = 3)

ggsave("AsterRegressions_Survival_perPop.pdf", plots_combined, width = 10, height = 7)


# Create a list to store diagnostic plots
diagnostic_plots <- list()

# Loop through each model in model_list
for (x_var in names(model_list)) {
  
  model <- model_list[[x_var]]
  resid <- residuals(model)
  fitted <- fitted(model)
  
  # --- QQ Plot of residuals ---
  qq_data <- data.frame(
    Theoretical = qqnorm(resid, plot.it = FALSE)$x,
    Sample = qqnorm(resid, plot.it = FALSE)$y
  )
  
  # Compute slope and intercept for qqline (like base R qqline)
  q_theoretical <- quantile(qq_data$Theoretical, probs = c(0.25, 0.75))
  q_sample <- quantile(qq_data$Sample, probs = c(0.25, 0.75))
  slope <- diff(q_sample) / diff(q_theoretical)
  intercept <- q_sample[1] - slope * q_theoretical[1]
  
  # --- QQ Plot with QQ Line ---
  qq_plot <- ggplot(qq_data, aes(x = Theoretical, y = Sample)) +
    geom_point() +
    geom_abline(slope = slope, intercept = intercept, color = "red", linetype = "dashed", linewidth = 0.8) +
    ggtitle(paste("QQ Plot of Residuals for", x_var)) +
    theme_bw()
  
  # --- Residuals vs Fitted Plot ---
  resid_plot <- ggplot(data.frame(Fitted = fitted, Residuals = resid),
                       aes(x = Fitted, y = Residuals)) +
    geom_point() +
    geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
    ggtitle(paste("Residuals vs Fitted for", x_var)) +
    xlab("Fitted Values") +
    ylab("Residuals") +
    theme_bw()
  
  # Combine both plots vertically
  combined_plot <- gridExtra::grid.arrange(qq_plot, resid_plot, ncol = 1)
  
  diagnostic_plots[[x_var]] <- combined_plot
}

# Save all diagnostic plots to a single PDF

plots_combined <- marrangeGrob(grobs = diagnostic_plots, ncol = 2, nrow = 2)

ggsave("AsterRegressions_Survival_diagnostic_perPop.pdf", plots_combined, width = 10, height = 7)
```

#plotting
```{r}
library(cowplot)
a <- ggplot(fitness_df, aes(x = TD, y = mu)) +
  geom_point()+theme(panel.background = element_blank(), panel.grid.major =    element_line("grey"), panel.border = element_rect(color = "black", fill = NA)) +
     theme(axis.text.x = element_text(angle = 0, hjust = 1)) +
    labs(y = "Mean predicted fitness (mu)", x = "Continentality (C)") + geom_smooth(method = "lm", se = T)
b <- ggplot(fitness_df, aes(x = TD, y = Height)) +
  geom_point()+theme(panel.background = element_blank(), panel.grid.major =    element_line("grey"), panel.border = element_rect(color = "black", fill = NA)) +
     theme(axis.text.x = element_text(angle = 0, hjust = 1)) +
    labs(y = "Mean predicted Height", x = "Continentality (C)")+ geom_smooth(method = "lm", se = T)
c <- ggplot(fitness_df, aes(x = TD, y = Survival)) +
  geom_point()+theme(panel.background = element_blank(), panel.grid.major =    element_line("grey"), panel.border = element_rect(color = "black", fill = NA)) +
     theme(axis.text.x = element_text(angle = 0, hjust = 1)) +
    labs(y = "Mean predicted survival", x = "Continentality (C)")+ geom_smooth(method = "lm", se = T) 

plot <- plot_grid(c,b,a, labels = c("A","B","C"), ncol = 3, nrow = 2, align = "h")

modelA <- lm(mu~DD5, data = fitness_df)
summary(modelA)
modelB <- lm(Height~DD5, data = fitness_df)
summary(modelB)
modelC <- lm(Survival~DD5, data = fitness_df)
summary(modelC)
modelD <- lm(mu~TD, data = fitness_df)
summary(modelD)
modelE <- lm(Height~TD, data = fitness_df)
summary(modelE)
modelF <- lm(Survival~TD, data = fitness_df)
summary(modelF)

```