---
title: "FRANIG Seed Morphology - Narrow Sense Heritability & Variance Partitioning"
author: "KyraL"
date: "2026-01-06"
output: html_document
---
#Introduction
Here we calculate variance explained by population, family, and residual (within tree) variance for the traits measured in the greenhouse. We also calculate narrow sense heritability and additive genetic variance for each trait.

#Read in data
```{r}
library(readxl)
library(tidyverse)
#time to emergence, true leaves, and compound leaves was done in excel because dates are hard to work with
FRANIGCG_2024_LifeHistoryRawData <- read_excel("~/GitHub/Ash/FRANIG_Seed/FRANIGCG_2024_LifeHistoryRawData.xlsx")
Fall2024_HeightData <- read_excel("~/GitHub/Ash/FRANIG_Seed/Fall2024_HeightData.xlsx")

#clean greenhouse data
#remove entries where no seed was planted
FRANIGCG_2024_LifeHistoryRawData <- FRANIGCG_2024_LifeHistoryRawData[FRANIGCG_2024_LifeHistoryRawData$Emergence_Date_MMDDYY != "no seed" | is.na(FRANIGCG_2024_LifeHistoryRawData$Emergence_Date_MMDDYY),]

#remove unnecessary columns
pheno_cleaned <- FRANIGCG_2024_LifeHistoryRawData[,c(3:10,26:28)] #keep seed ID for now

#create a seed ID column in the height sheet
Fall2024_HeightData$Seed_ID <- paste(Fall2024_HeightData$Maternal_ID,Fall2024_HeightData$Seed_No, sep = "-")

#remove unnecessary columns
height_cleaned <- Fall2024_HeightData[,c(8,11)]

#merge data frames
df <- full_join(pheno_cleaned, height_cleaned, by = "Seed_ID")
df$`Height(cm)` <- as.numeric(df$`Height(cm)`)

```


#Heritability Estimates
##Emergence Timing

```{r}
#filter out entries with no emergence data
Emergence.df <- df %>% filter(Time_to_Emergence > 0)

#is the trait normal?
hist(Emergence.df$Time_to_Emergence)
qqnorm(Emergence.df$Time_to_Emergence)
qqline(Emergence.df$Time_to_Emergence)

#log transform to correct right skew
Emergence.df$log_emerge <- log(Emergence.df$Time_to_Emergence)

hist(Emergence.df$log_emerge)
qqnorm(Emergence.df$log_emerge)
qqline(Emergence.df$log_emerge)

Emergence.df$sqrt_emerge <- sqrt(Emergence.df$Time_to_Emergence)

hist(Emergence.df$sqrt_emerge)
qqnorm(Emergence.df$sqrt_emerge)
qqline(Emergence.df$sqrt_emerge)

library(lme4)
#code adapted from Volk et al 2022 AJB
Emergence.df$Provenance <- as.factor(Emergence.df$Provenance)
Emergence.df$Individual <- as.factor(Emergence.df$Individual)
Emergence.df$Table <- as.factor(Emergence.df$Table)

#model emergence with provenance, maternal family, and table as random effects so we can pull out the variance components
emerge.mod <- lmer(log_emerge ~ (1|Provenance)+ (1|Provenance:Individual) + (1|Table), data = Emergence.df)
summary(emerge.mod)

# Extract residuals and fitted values
resid_vals  <- resid(emerge.mod)
fitted_vals <- fitted(emerge.mod)

diag_df <- data.frame(
  fitted = fitted_vals,
  resid  = resid_vals
)

## 1. Homoscedasticity: Residuals vs Fitted
p1 <- ggplot(diag_df, aes(x = fitted, y = resid)) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_classic() +
  labs(
    title = "Residuals vs Fitted",
    x = "Fitted values",
    y = "Residuals"
  )

## 2. Q–Q plot of residuals
p2 <- ggplot(diag_df, aes(sample = resid)) +
  stat_qq() +
  stat_qq_line() +
  theme_classic() +
  labs(
    title = "Normal Q–Q Plot of Residuals",
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  )

# Print plots
p1
p2
#the homoscedasticity still looks a bit off, so we may be missing a random effect

vars <- as.data.frame(VarCorr(emerge.mod))
#half siblings
emerge.h2 <- (4*vars[1,4])/ (vars[1,4]+vars[2,4]+vars[3,4]+vars[4,4])
emerge.h2
emerge.VA <- (4*vars[1,4])
#full siblings
emerge.h2 <- (2*vars[1,4]/ (vars[1,4]+vars[2,4]+vars[3,4]))
emerge.h2
emerge.VA <- (2*vars[1,4])
mean.emerge <- mean(Emergence.df$log_emerge)


get_h2 <- function(mod) {
  vc <- as.data.frame(VarCorr(mod))
  
  sigProv <- vc$vcov[vc$grp == "Provenance"]
  sigInd  <- vc$vcov[vc$grp == "Provenance:Individual"]  # keep interaction for family
  sigTable <- vc$vcov[vc$grp == "Table"]
  sige    <- attr(VarCorr(mod), "sc")^2
  
  # Assuming half-sibs: h2 = 4 * VA / VP
  h2 <- 4 * sigInd / (sigProv + sigInd + sigTable + sige)
  
  return(h2)
}

#parametric bootstrap to estimate SE and CIs
set.seed(123)

boot_h2 <- bootMer(
  emerge.mod,
  FUN = get_h2,
  nsim = 1000,
  type = "parametric",
  use.u = FALSE
)

# Standard error
se_h2 <- sd(boot_h2$t)
se_h2

# 95% CI
quantile(boot_h2$t, c(0.025, 0.975))
```


##True leaf timing
```{r}
#remove entries with no true leaf date or entries that had no emergence time to use to calculate true leaf timing
TrueLeaves.df <- FRANIGCG_2024_LifeHistoryRawData %>% filter(Time_to_TrueLeaves > 0)
TrueLeaves.df <- TrueLeaves.df %>% filter(Time_to_TrueLeaves < 1000)

#is the trait normal?
hist(TrueLeaves.df$Time_to_TrueLeaves)
qqnorm(TrueLeaves.df$Time_to_TrueLeaves)
qqline(TrueLeaves.df$Time_to_TrueLeaves)

#log transform to fix the right skew
TrueLeaves.df$log_true <- log(TrueLeaves.df$Time_to_TrueLeaves)

hist(TrueLeaves.df$log_true)
qqnorm(TrueLeaves.df$log_true)
qqline(TrueLeaves.df$log_true)


```

```{r}
library(lme4)
#code adapted from Volk et al 2022 AJB
TrueLeaves.df$Provenance <- as.factor(TrueLeaves.df$Provenance)
TrueLeaves.df$Individual <- as.factor(TrueLeaves.df$Individual)
TrueLeaves.df$Table <- as.factor(TrueLeaves.df$Table)

#model emergence with provenance, maternal famil, and table as random effects so we can pull out the variance components
true.mod <- lmer(log_true ~ (1|Provenance)+ (1|Individual)+ (1|Table), data = TrueLeaves.df)
summary(true.mod)

# Extract residuals and fitted values
resid_vals  <- resid(true.mod)
fitted_vals <- fitted(true.mod)

diag_df <- data.frame(
  fitted = fitted_vals,
  resid  = resid_vals
)

## 1. Homoscedasticity: Residuals vs Fitted
p1 <- ggplot(diag_df, aes(x = fitted, y = resid)) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_classic() +
  labs(
    title = "Residuals vs Fitted",
    x = "Fitted values",
    y = "Residuals"
  )

## 2. Q–Q plot of residuals
p2 <- ggplot(diag_df, aes(sample = resid)) +
  stat_qq() +
  stat_qq_line() +
  theme_classic() +
  labs(
    title = "Normal Q–Q Plot of Residuals",
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  )

# Print plots
p1
p2
#the homoscedasticity still looks a bit off, so we may be missing a random effect

vars <- as.data.frame(VarCorr(true.mod))
true.h2 <- (4*vars[1,4]/ (vars[1,4]+vars[2,4]+vars[3,4] + vars[4,4]))
true.h2
true.VA <- (4*vars[1,4])
mean.true <- mean(TrueLeaves.df$true.mod)


#parametric bootstrap to estimate SE and CIs
set.seed(123)

boot_h2 <- bootMer(
  true.mod,
  FUN = get_h2,
  nsim = 1000,
  type = "parametric",
  use.u = FALSE
)

# Standard error
se_h2 <- sd(boot_h2$t)
se_h2

# 95% CI
quantile(boot_h2$t, c(0.025, 0.975))
```

##compound leaf timing
```{r}
#remove entries with no compound leaf date or those missing a true leaf date to calculate time to compound leaves
CompLeaves.df <- FRANIGCG_2024_LifeHistoryRawData %>% filter(Time_to_CompoundLeaves > 0)
CompLeaves.df <- CompLeaves.df %>% filter(Time_to_CompoundLeaves < 1000)

#is the trait normal?
hist(CompLeaves.df$Time_to_CompoundLeaves)
qqnorm(CompLeaves.df$Time_to_CompoundLeaves)
qqline(CompLeaves.df$Time_to_CompoundLeaves)

#does a log transform fix the right skew?
CompLeaves.df$log_comp <- log(CompLeaves.df$Time_to_CompoundLeaves)

hist(CompLeaves.df$log_comp)
qqnorm(CompLeaves.df$log_comp)
qqline(CompLeaves.df$log_comp)


```

```{r}
library(lme4)
#code adapted from Volk et al 2022 AJB
CompLeaves.df$Provenance <- as.factor(CompLeaves.df$Provenance)
CompLeaves.df$Individual <- as.factor(CompLeaves.df$Individual)
CompLeaves.df$Table <- as.factor(CompLeaves.df$Table)

#model emergence with provenance, maternal family, and table as random effects so we can pull out the variance components
comp.mod <- lmer(log_comp ~ (1|Provenance)+ (1|Individual) + (1|Table), data = CompLeaves.df)
summary(comp.mod)

# Extract residuals and fitted values
resid_vals  <- resid(comp.mod)
fitted_vals <- fitted(comp.mod)

diag_df <- data.frame(
  fitted = fitted_vals,
  resid  = resid_vals
)

## 1. Homoscedasticity: Residuals vs Fitted
p1 <- ggplot(diag_df, aes(x = fitted, y = resid)) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_classic() +
  labs(
    title = "Residuals vs Fitted",
    x = "Fitted values",
    y = "Residuals"
  )

## 2. Q–Q plot of residuals
p2 <- ggplot(diag_df, aes(sample = resid)) +
  stat_qq() +
  stat_qq_line() +
  theme_classic() +
  labs(
    title = "Normal Q–Q Plot of Residuals",
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  )

# Print plots
p1
p2
#the homoscedasticity still looks a bit off, so we may be missing a random effect

vars <- as.data.frame(VarCorr(comp.mod))
comp.h2 <- (4*vars[1,4]/ (vars[1,4]+vars[2,4]+vars[3,4]+ vars[4,4]))
comp.h2
comp.VA <- (4*vars[1,4])
mean.comp <- mean(TrueLeaves.df$comp.mod)


#parametric bootstrap to estimate SE and CIs
set.seed(123)

boot_h2 <- bootMer(
  comp.mod,
  FUN = get_h2,
  nsim = 1000,
  type = "parametric",
  use.u = FALSE
)

# Standard error
se_h2 <- sd(boot_h2$t)
se_h2

# 95% CI
quantile(boot_h2$t, c(0.025, 0.975))
```

##height
```{r}
#remove entries with no height value
Height.df <- df %>% filter(`Height(cm)` > 0)

#is the trait normally distributed?
hist(Height.df$`Height(cm)`)
qqnorm(Height.df$`Height(cm)`)
qqline(Height.df$`Height(cm)`)

#log transorm to fix the skew
Height.df$log_height <- log(Height.df$`Height(cm)`)

hist(Height.df$log_height)
qqnorm(Height.df$log_height)
qqline(Height.df$log_height)


```

```{r}
library(lme4)
#code adapted from Volk et al 2022 AJB
Height.df$Provenance <- as.factor(Height.df$Provenance)
Height.df$Individual <- as.factor(Height.df$Individual)
Height.df$Table <- as.factor(Height.df$Table)


#model emergence with provenance, maternal family, and table as random effects so we can pull out the variance components
height.mod <- lmer(log_height ~ (1|Provenance)+ (1|Provenance:Individual) + (1|Table), data = Height.df)
summary(height.mod)

# Extract residuals and fitted values
resid_vals  <- resid(height.mod)
fitted_vals <- fitted(height.mod)

diag_df <- data.frame(
  fitted = fitted_vals,
  resid  = resid_vals
)

## 1. Homoscedasticity: Residuals vs Fitted
p1 <- ggplot(diag_df, aes(x = fitted, y = resid)) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_classic() +
  labs(
    title = "Residuals vs Fitted",
    x = "Fitted values",
    y = "Residuals"
  )

## 2. Q–Q plot of residuals
p2 <- ggplot(diag_df, aes(sample = resid)) +
  stat_qq() +
  stat_qq_line() +
  theme_classic() +
  labs(
    title = "Normal Q–Q Plot of Residuals",
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  )

# Print plots
p1
p2
#the homoscedasticity still looks a bit off, so we may be missing a random effect

vars <- as.data.frame(VarCorr(height.mod))
height.h2 <- (4*vars[1,4])/ (vars[1,4]+vars[2,4]+vars[3,4] + vars[4,4])
height.h2
height.VA <- (4*vars[1,4])
mean.height <- mean(Height.df$height.mod)


#parametric bootstrap to estimate SE and CIs
set.seed(123)

boot_h2 <- bootMer(
  height.mod,
  FUN = get_h2,
  nsim = 1000,
  type = "parametric",
  use.u = FALSE
)

# Standard error
se_h2 <- sd(boot_h2$t)
se_h2

# 95% CI
quantile(boot_h2$t, c(0.025, 0.975))
```

###testing 
The heritability value for height seems extremely high. This code was used to test how the addition of table as a random effect, log transforming the data, and using different relatedness coefficients affected heritability values. We found that log transformation does inflate heritability because it transforms the variance components. We also see that adding Table as a fixed effect explains additional variance. Finally, we report in the main text heritability values for r = 1/4 assuming half sibling relationships. Given that seeds may be more related than that, we report heritability ar r = 1/2 (full sibligs) as a lower estimate of heritability.
```{r}
Height.df$Provenance <- as.factor(Height.df$Provenance)
Height.df$Individual <- as.factor(Height.df$Individual)
Height.df$Table <- as.factor(Height.df$Table)

#testing the addition of table
height.mod1 <- lmer(`Height(cm)` ~ (1|Provenance)+ (1|Provenance:Individual), data = Height.df)
height.mod2 <- lmer(`Height(cm)` ~ (1|Provenance)+ (1|Provenance:Individual) + (1|Table), data = Height.df)

plot(height.mod1)
qqnorm(resid(height.mod1))
qqline(resid(height.mod1))

plot(height.mod2)
qqnorm(resid(height.mod2))
qqline(resid(height.mod2))

vars1 <- as.data.frame(VarCorr(height.mod1))
height.h2.1 <- (4*vars1[1,4])/ (vars1[1,4]+vars1[2,4]+vars1[3,4])
height.h2.1

vars2 <- as.data.frame(VarCorr(height.mod2))
height.h2.2 <- (4*vars2[1,4])/ (vars2[1,4]+vars2[2,4]+vars2[3,4]+vars2[4,4])
height.h2.2

#Testing the addition of table with the log transformed trait
height.mod3 <- lmer(log_height ~ (1|Provenance)+ (1|Provenance:Individual), data = Height.df)
height.mod4 <- lmer(log_height ~ (1|Provenance)+ (1|Provenance:Individual) + (1|Table), data = Height.df)

plot(height.mod3)
qqnorm(resid(height.mod3))
qqline(resid(height.mod3))

plot(height.mod4)
qqnorm(resid(height.mod4))
qqline(resid(height.mod4))

vars3 <- as.data.frame(VarCorr(height.mod3))
height.h2.3 <- (4*vars3[1,4])/ (vars3[1,4]+vars3[2,4]+vars3[3,4])
height.h2.3

vars4 <- as.data.frame(VarCorr(height.mod4))
height.h2.4 <- (4*vars4[1,4])/ (vars4[1,4]+vars4[2,4]+vars4[3,4]+vars4[4,4])
height.h2.4

#try adding seed weight as a fixed effect to account for maternal provisioning

FRANIG_SeedMorphology_AllTraits <- read_csv("~/GitHub/Ash/FRANIG_Seed/FRANIG_SeedMorphology_AllTraits.csv")
FRANIG_SeedMorphology_AllTraits$Seed_Weight <- as.numeric(FRANIG_SeedMorphology_AllTraits$Seed_Weight)
colnames(FRANIG_SeedMorphology_AllTraits)[3] <- "Individual"

seed_weight <- aggregate(Seed_Weight ~ Individual, data = FRANIG_SeedMorphology_AllTraits, FUN = mean)

height.df <- left_join(Height.df, seed_weight, by = "Individual")

height.mod5 <- lmer(log_height ~ Seed_Weight + (1|Provenance)+ (1|Provenance:Individual) + (1|Table), data = height.df)
```

##full sibling heritability estimates
```{r, cache=TRUE}
vars <- as.data.frame(VarCorr(emerge.mod))
emerge.h2 <- (2*vars4[1,4])/ (vars4[1,4]+vars4[2,4]+vars4[3,4]+vars4[4,4])
emerge.h2
emerge.VA <- (2*vars[1,4])

get_h2 <- function(mod) {
  vc <- as.data.frame(VarCorr(mod))
  
  sigProv <- vc$vcov[vc$grp == "Provenance"]
  sigInd  <- vc$vcov[vc$grp == "Provenance:Individual"]  # keep interaction for family
  sigTable <- vc$vcov[vc$grp == "Table"]
  sige    <- attr(VarCorr(mod), "sc")^2
  
  # Assuming full-sibs: h2 = 2 * VA / VP
  h2 <- 2 * sigInd / (sigProv + sigInd + sigTable + sige)
  
  return(h2)
}

set.seed(123)

boot_h2 <- bootMer(
  emerge.mod,
  FUN = get_h2,
  nsim = 1000,
  type = "parametric",
  use.u = FALSE
)

# Standard error
se_h2 <- sd(boot_h2$t)
se_h2

# 95% CI
quantile(boot_h2$t, c(0.025, 0.975))
```

#Variance Partitioning
```{r}
#code adapted from Volk et al 2022 & DiSanto et al 2021
library(sjPlot)
library(lme4)
library(performance)
library(see)
library(lmerTest)
library(MuMIn)

res <- matrix(nrow = 4, ncol = 4)
#make matrix with r squared values for each seed measurement (i.e. 4 rows (traits) and 3 columns (r-squared values))
rownames(res) <- colnames(df[9:12])
colnames(res) <- c("R2_Pop", "R2_MatFam", "R2_Tot", "R2_Err")

pval <- matrix(nrow = 4, ncol = 2)
rownames(pval) <- colnames(df[9:12])
colnames(pval) <- c("Pop", "MatFam")

#emergence
emerge <- lmer(log_emerge ~ Provenance + (1|Provenance:Individual), data = Emergence.df)

emerge_var <- r.squaredGLMM(emerge)
res[1,1] <- emerge_var[,1]
res[1,2] <- (emerge_var[,2] - emerge_var[,1])
res[1,3] <- emerge_var[,2]
res[1,4] <- 1 - emerge_var[,2]

pval[1,1] <- anova(emerge)$`Pr(>F)`
pval[1,2] <- ranova(emerge)$`Pr(>Chisq)`[2]

#true leaves
true <- lmer(log_true ~ Provenance + (1|Provenance:Individual), data = TrueLeaves.df)

true_var <- r.squaredGLMM(true)
res[2,1] <- true_var[,1]
res[2,2] <- (true_var[,2] - true_var[,1])
res[2,3] <- true_var[,2]
res[2,4] <- 1 - true_var[,2]

pval[2,1] <- anova(true)$`Pr(>F)`
pval[2,2] <- ranova(true)$`Pr(>Chisq)`[2]

#compound leaves
comp <- lmer(log_comp ~ Provenance + (1|Provenance:Individual), data = CompLeaves.df)

comp_var <- r.squaredGLMM(comp)
res[3,1] <- comp_var[,1]
res[3,2] <- (comp_var[,2] - comp_var[,1])
res[3,3] <- comp_var[,2]
res[3,4] <- 1 - comp_var[,2]

pval[3,1] <- anova(comp)$`Pr(>F)`
pval[3,2] <- ranova(comp)$`Pr(>Chisq)`[2]

#height
height <- lmer(log_height ~ Provenance + (1|Provenance:Individual), data = Height.df)

height_var <- r.squaredGLMM(height)
res[4,1] <- height_var[,1]
res[4,2] <- (height_var[,2] - height_var[,1])
res[4,3] <- height_var[,2]
res[4,4] <- 1 - height_var[,2]

pval[4,1] <- anova(height)$`Pr(>F)`
pval[4,2] <- ranova(height)$`Pr(>Chisq)`[2]

write.csv(res, file = "LifeHistoryTraits_VariancePartitioning.csv")


#does adding table as a random effect change variance partitioning results?
get_var_partition <- function(model) {
  vc <- as.data.frame(VarCorr(model))
  
  vars <- setNames(vc$vcov, vc$grp)
  total <- sum(vars)
  
  props <- vars / total
  
  return(props)
}
emerge_vp <- lmer(log_emerge ~ 1 + (1|Provenance) + (1|Provenance:Individual) + (1|Table), data = Emergence.df)
true_vp   <- lmer(log_true   ~ 1 + (1|Provenance) + (1|Provenance:Individual) + (1|Table), data = TrueLeaves.df)
comp_vp   <- lmer(log_comp   ~ 1 + (1|Provenance) + (1|Provenance:Individual) + (1|Table), data = CompLeaves.df)
height_vp <- lmer(log_height ~ 1 + (1|Provenance) + (1|Provenance:Individual) + (1|Table), data = Height.df)

res <- rbind(
  get_var_partition(emerge_vp),
  get_var_partition(true_vp),
  get_var_partition(comp_vp),
  get_var_partition(height_vp)
)

write.csv(res, "LifeHistoryTraits_VariancePartitioning_withTable.csv")

```


