---
title: "FRANIG Seed Morphology - Repeatability Estimates"
output: html_notebook
---
#Introduction
This portion of code was used to calculate repeatability estimates for each seed morphology trait for each population. The first part of the code was used to test how estimates of typical narrow sense heritability differed from repeatbility. The remainder of the code is calculating repeatability and performing bootstrapping.

#Read in data
```{r}
library(readxl)
library(tidyverse)

#read in seed morphology data
FRANIG_SeedMorphology_AllTraits <- read_csv("~/GitHub/Ash/FRANIG_Seed/FRANIG_SeedMorphology_AllTraits.csv")
df <- FRANIG_SeedMorphology_AllTraits[,c(3:9,11,16:21)]
colnames(df) <- c("Family", "Wing_Area", "Wing_Length", "Wing_Width", "Seed_Area","Seed_Length", "Seed_Width", "Provenance", "Latitude", "Longitude", "Elevation", "Year_collected", "SeedtoWing_Area", "Wing_LengthtoWidth")
df$Provenance <- as.factor(df$Provenance)
df$Family <- as.factor(df$Family)
df$Wing_Area <- as.numeric(df$Wing_Area)

#look at distribution of raw data
hist(df$Wing_Area)
hist(df$Wing_Width)
hist(df$Wing_Length)
hist(df$Seed_Area)
hist(df$Seed_Length)
hist(df$Seed_Width)
hist(df$SeedtoWing_Area)
hist(df$Wing_LengthtoWidth)

```

#Calculating Repeatability, CIs and SEs
For each trait, observed repeatability was calculated for each provenance and averaged across provenances to get a mean repeatability per trait. Then, a population level bootstrap with resampling was performed for each trait to get estimates of uncertainty for repeatability estimates.
```{r}
library(lme4)
library(parallel)

#wing area
# Function to compute ICC (H2) for each provenance
get_H2 <- function(df) {
  sapply(levels(df$Provenance), function(p) {
    dsub <- subset(df, Provenance == p)
    # catch cases with too few families
    if(length(unique(dsub$Family)) < 2) return(NA)
    m <- try(lmer(Wing_Area ~ (1|Family), data = dsub), silent = TRUE)
    if(inherits(m, "try-error")) return(NA)
    vars <- as.data.frame(VarCorr(m))
    fam_var <- vars[vars$grp == "Family", "vcov"]
    res_var <- vars[vars$grp == "Residual", "vcov"]
    H2 <- (fam_var) / (fam_var + res_var)
    return(H2)
  })
}

# 1. Observed average ICC
obs_WAH2 <- get_H2(df)
obs_WAmean <- mean(obs_WAH2, na.rm = TRUE)

# 2. Parallel stratified bootstrap
set.seed(123)
nboot <- 1000
ncores <- detectCores() - 1
cl <- makeCluster(ncores)

clusterExport(cl, varlist = c("df", "get_H2"), envir = environment())
clusterEvalQ(cl, library(lme4))

boot_WAmeans <- parLapply(cl, 1:nboot, function(i) {
  # --- resample families within each provenance ---
  df_boot <- do.call(rbind, lapply(split(df, df$Provenance), function(dsub) {
    fams <- unique(dsub$Family)                                 # list of families
    sampled_fams <- sample(fams, length(fams), replace = TRUE)  # resample families with replacement
    do.call(rbind, lapply(sampled_fams, function(f) {
      dsub[dsub$Family == f, ]                                  # include all individuals from each sampled family
    }))
  }))
  
  # --- compute h2 per provenance for the bootstrap sample ---
  H2_boot <- get_H2(df_boot)
  
  # --- average across provenances ---
  mean(H2_boot, na.rm = TRUE)
})

boot_WAmeans <- unlist(boot_WAmeans)

# 3. CI
WAci <- quantile(boot_WAmeans, probs = c(0.025, 0.975), na.rm = TRUE)

list(
  observed_mean = obs_WAmean,
  bootstrap_se = sd(boot_WAmeans, na.rm = TRUE),
  ci_95 = WAci
)

# 4. Plot bootstrap distribution
boot_WAdf <- data.frame(mean_H2 = boot_WAmeans)

pWA <- ggplot(boot_WAdf, aes(x = mean_H2)) +
  geom_histogram(bins = 40, fill = "skyblue", color = "white", alpha = 0.7) +
  geom_vline(xintercept = obs_WAmean, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = WAci, color = "darkblue", linetype = "dotted", size = 1) +
  labs(
    title = "Bootstrap distribution of mean wing area ICC (H²)",
    x = "Mean ICC (bootstrap samples)",
    y = "Frequency"
  ) +
  theme_minimal()

print(pWA)

#Wing length
# Function to compute ICC (H2) for each provenance
get_H2 <- function(df) {
  sapply(levels(df$Provenance), function(p) {
    dsub <- subset(df, Provenance == p)
    # catch cases with too few families
    if(length(unique(dsub$Family)) < 2) return(NA)
    m <- try(lmer(Wing_Length ~ (1|Family), data = dsub), silent = TRUE)
    if(inherits(m, "try-error")) return(NA)
    vars <- as.data.frame(VarCorr(m))
    fam_var <- vars[vars$grp == "Family", "vcov"]
    res_var <- vars[vars$grp == "Residual", "vcov"]
    H2 <- (fam_var) / (fam_var + res_var)
    return(H2)
  })
}

# 1. Observed average ICC
obs_WLH2 <- get_H2(df)
obs_WLmean <- mean(obs_WLH2, na.rm = TRUE)

# 2. Parallel stratified bootstrap
set.seed(123)
nboot <- 1000
ncores <- detectCores() - 1
cl <- makeCluster(ncores)

clusterExport(cl, varlist = c("df", "get_H2"), envir = environment())
clusterEvalQ(cl, library(lme4))

boot_WLmeans <- parLapply(cl, 1:nboot, function(i) {
  # --- resample families within each provenance ---
  df_boot <- do.call(rbind, lapply(split(df, df$Provenance), function(dsub) {
    fams <- unique(dsub$Family)                                 # list of families
    sampled_fams <- sample(fams, length(fams), replace = TRUE)  # resample families with replacement
    do.call(rbind, lapply(sampled_fams, function(f) {
      dsub[dsub$Family == f, ]                                  # include all individuals from each sampled family
    }))
  }))
  
  # --- compute h2 per provenance for the bootstrap sample ---
  H2_boot <- get_H2(df_boot)
  
  # --- average across provenances ---
  mean(H2_boot, na.rm = TRUE)
})

boot_WLmeans <- unlist(boot_WLmeans)

# 3. CI
WLci <- quantile(boot_WLmeans, probs = c(0.025, 0.975), na.rm = TRUE)

list(
  observed_mean = obs_WLmean,
  bootstrap_se = sd(boot_WLmeans, na.rm = TRUE),
  ci_95 = WLci
)

# 4. Plot bootstrap distribution
boot_WLdf <- data.frame(mean_H2 = boot_WLmeans)

pWL <- ggplot(boot_WLdf, aes(x = mean_H2)) +
  geom_histogram(bins = 40, fill = "skyblue", color = "white", alpha = 0.7) +
  geom_vline(xintercept = obs_WLmean, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = WLci, color = "darkblue", linetype = "dotted", size = 1) +
  labs(
    title = "Bootstrap distribution of mean wing length ICC (H²)",
    x = "Mean ICC (bootstrap samples)",
    y = "Frequency"
  ) +
  theme_minimal()

print(pWL)

#Wing width
# Function to compute ICC (H2) for each provenance
get_H2 <- function(df) {
  sapply(levels(df$Provenance), function(p) {
    dsub <- subset(df, Provenance == p)
    # catch cases with too few families
    if(length(unique(dsub$Family)) < 2) return(NA)
    m <- try(lmer(Wing_Width ~ (1|Family), data = dsub), silent = TRUE)
    if(inherits(m, "try-error")) return(NA)
    vars <- as.data.frame(VarCorr(m))
    fam_var <- vars[vars$grp == "Family", "vcov"]
    res_var <- vars[vars$grp == "Residual", "vcov"]
    H2 <- (fam_var) / (fam_var + res_var)
    return(H2)
  })
}

# 1. Observed average ICC
obs_WWH2 <- get_H2(df)
obs_WWmean <- mean(obs_WWH2, na.rm = TRUE)

# 2. Parallel stratified bootstrap
set.seed(123)
nboot <- 1000
ncores <- detectCores() - 1
cl <- makeCluster(ncores)

clusterExport(cl, varlist = c("df", "get_H2"), envir = environment())
clusterEvalQ(cl, library(lme4))

boot_WWmeans <- parLapply(cl, 1:nboot, function(i) {
  # --- resample families within each provenance ---
  df_boot <- do.call(rbind, lapply(split(df, df$Provenance), function(dsub) {
    fams <- unique(dsub$Family)                                 # list of families
    sampled_fams <- sample(fams, length(fams), replace = TRUE)  # resample families with replacement
    do.call(rbind, lapply(sampled_fams, function(f) {
      dsub[dsub$Family == f, ]                                  # include all individuals from each sampled family
    }))
  }))
  
  # --- compute h2 per provenance for the bootstrap sample ---
  H2_boot <- get_H2(df_boot)
  
  # --- average across provenances ---
  mean(H2_boot, na.rm = TRUE)
})

boot_WWmeans <- unlist(boot_WWmeans)

# 3. CI
WWci <- quantile(boot_WWmeans, probs = c(0.025, 0.975), na.rm = TRUE)

list(
  observed_mean = obs_WWmean,
  bootstrap_se = sd(boot_WWmeans, na.rm = TRUE),
  ci_95 = WWci
)

# 4. Plot bootstrap distribution
boot_WWdf <- data.frame(mean_H2 = boot_WWmeans)

pWW <- ggplot(boot_WWdf, aes(x = mean_H2)) +
  geom_histogram(bins = 40, fill = "skyblue", color = "white", alpha = 0.7) +
  geom_vline(xintercept = obs_WWmean, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = WWci, color = "darkblue", linetype = "dotted", size = 1) +
  labs(
    title = "Bootstrap distribution of mean wing width ICC (H²)",
    x = "Mean ICC (bootstrap samples)",
    y = "Frequency"
  ) +
  theme_minimal()

print(pWW)

#seed area
# Function to compute ICC (H2) for each provenance
get_H2 <- function(df) {
  sapply(levels(df$Provenance), function(p) {
    dsub <- subset(df, Provenance == p)
    # catch cases with too few families
    if(length(unique(dsub$Family)) < 2) return(NA)
    m <- try(lmer(Seed_Area ~ (1|Family), data = dsub), silent = TRUE)
    if(inherits(m, "try-error")) return(NA)
    vars <- as.data.frame(VarCorr(m))
    fam_var <- vars[vars$grp == "Family", "vcov"]
    res_var <- vars[vars$grp == "Residual", "vcov"]
    H2 <- (fam_var) / (fam_var + res_var)
    return(H2)
  })
}

# 1. Observed average ICC
obs_SAH2 <- get_H2(df)
obs_SAmean <- mean(obs_SAH2, na.rm = TRUE)

# 2. Parallel stratified bootstrap
set.seed(123)
nboot <- 1000
ncores <- detectCores() - 1
cl <- makeCluster(ncores)

clusterExport(cl, varlist = c("df", "get_H2"), envir = environment())
clusterEvalQ(cl, library(lme4))

boot_SAmeans <- parLapply(cl, 1:nboot, function(i) {
  # --- resample families within each provenance ---
  df_boot <- do.call(rbind, lapply(split(df, df$Provenance), function(dsub) {
    fams <- unique(dsub$Family)                                 # list of families
    sampled_fams <- sample(fams, length(fams), replace = TRUE)  # resample families with replacement
    do.call(rbind, lapply(sampled_fams, function(f) {
      dsub[dsub$Family == f, ]                                  # include all individuals from each sampled family
    }))
  }))
  
  # --- compute h2 per provenance for the bootstrap sample ---
  H2_boot <- get_H2(df_boot)
  
  # --- average across provenances ---
  mean(H2_boot, na.rm = TRUE)
})

boot_SAmeans <- unlist(boot_SAmeans)

# 3. CI
SAci <- quantile(boot_SAmeans, probs = c(0.025, 0.975), na.rm = TRUE)

list(
  observed_mean = obs_SAmean,
  bootstrap_se = sd(boot_SAmeans, na.rm = TRUE),
  ci_95 = SAci
)

# 4. Plot bootstrap distribution
boot_SAdf <- data.frame(mean_H2 = boot_SAmeans)

pSA <- ggplot(boot_SAdf, aes(x = mean_H2)) +
  geom_histogram(bins = 40, fill = "skyblue", color = "white", alpha = 0.7) +
  geom_vline(xintercept = obs_SAmean, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = SAci, color = "darkblue", linetype = "dotted", size = 1) +
  labs(
    title = "Bootstrap distribution of mean seed area ICC (H²)",
    x = "Mean ICC (bootstrap samples)",
    y = "Frequency"
  ) +
  theme_minimal()

print(pSA)

#seed length
# Function to compute ICC (H2) for each provenance
get_H2 <- function(df) {
  sapply(levels(df$Provenance), function(p) {
    dsub <- subset(df, Provenance == p)
    # catch cases with too few families
    if(length(unique(dsub$Family)) < 2) return(NA)
    m <- try(lmer(Seed_Length ~ (1|Family), data = dsub), silent = TRUE)
    if(inherits(m, "try-error")) return(NA)
    vars <- as.data.frame(VarCorr(m))
    fam_var <- vars[vars$grp == "Family", "vcov"]
    res_var <- vars[vars$grp == "Residual", "vcov"]
    H2 <- (fam_var) / (fam_var + res_var)
    return(H2)
  })
}

# 1. Observed average ICC
obs_SLH2 <- get_H2(df)
obs_SLmean <- mean(obs_SLH2, na.rm = TRUE)

# 2. Parallel stratified bootstrap
set.seed(123)
nboot <- 1000
ncores <- detectCores() - 1
cl <- makeCluster(ncores)

clusterExport(cl, varlist = c("df", "get_H2"), envir = environment())
clusterEvalQ(cl, library(lme4))

boot_SLmeans <- parLapply(cl, 1:nboot, function(i) {
  # --- resample families within each provenance ---
  df_boot <- do.call(rbind, lapply(split(df, df$Provenance), function(dsub) {
    fams <- unique(dsub$Family)                                 # list of families
    sampled_fams <- sample(fams, length(fams), replace = TRUE)  # resample families with replacement
    do.call(rbind, lapply(sampled_fams, function(f) {
      dsub[dsub$Family == f, ]                                  # include all individuals from each sampled family
    }))
  }))
  
  # --- compute h2 per provenance for the bootstrap sample ---
  H2_boot <- get_H2(df_boot)
  
  # --- average across provenances ---
  mean(H2_boot, na.rm = TRUE)
})

boot_SLmeans <- unlist(boot_SLmeans)

# 3. CI
SLci <- quantile(boot_SLmeans, probs = c(0.025, 0.975), na.rm = TRUE)

list(
  observed_mean = obs_SLmean,
  bootstrap_se = sd(boot_SLmeans, na.rm = TRUE),
  ci_95 = SLci
)

# 4. Plot bootstrap distribution
boot_SLdf <- data.frame(mean_H2 = boot_SLmeans)

pSL <- ggplot(boot_SLdf, aes(x = mean_H2)) +
  geom_histogram(bins = 40, fill = "skyblue", color = "white", alpha = 0.7) +
  geom_vline(xintercept = obs_SLmean, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = SLci, color = "darkblue", linetype = "dotted", size = 1) +
  labs(
    title = "Bootstrap distribution of mean seed length ICC (H²)",
    x = "Mean ICC (bootstrap samples)",
    y = "Frequency"
  ) +
  theme_minimal()

print(pSL)

#seed width
# Function to compute ICC (H2) for each provenance
get_H2 <- function(df) {
  sapply(levels(df$Provenance), function(p) {
    dsub <- subset(df, Provenance == p)
    # catch cases with too few families
    if(length(unique(dsub$Family)) < 2) return(NA)
    m <- try(lmer(Seed_Width ~ (1|Family), data = dsub), silent = TRUE)
    if(inherits(m, "try-error")) return(NA)
    vars <- as.data.frame(VarCorr(m))
    fam_var <- vars[vars$grp == "Family", "vcov"]
    res_var <- vars[vars$grp == "Residual", "vcov"]
    H2 <- (fam_var) / (fam_var + res_var)
    return(H2)
  })
}

# 1. Observed average ICC
obs_SWH2 <- get_H2(df)
obs_SWmean <- mean(obs_SWH2, na.rm = TRUE)

# 2. Parallel stratified bootstrap
set.seed(123)
nboot <- 1000
ncores <- detectCores() - 1
cl <- makeCluster(ncores)

clusterExport(cl, varlist = c("df", "get_H2"), envir = environment())
clusterEvalQ(cl, library(lme4))

boot_SWmeans <- parLapply(cl, 1:nboot, function(i) {
  # --- resample families within each provenance ---
  df_boot <- do.call(rbind, lapply(split(df, df$Provenance), function(dsub) {
    fams <- unique(dsub$Family)                                 # list of families
    sampled_fams <- sample(fams, length(fams), replace = TRUE)  # resample families with replacement
    do.call(rbind, lapply(sampled_fams, function(f) {
      dsub[dsub$Family == f, ]                                  # include all individuals from each sampled family
    }))
  }))
  
  # --- compute h2 per provenance for the bootstrap sample ---
  H2_boot <- get_H2(df_boot)
  
  # --- average across provenances ---
  mean(H2_boot, na.rm = TRUE)
})

boot_SWmeans <- unlist(boot_SWmeans)

# 3. CI
SWci <- quantile(boot_SWmeans, probs = c(0.025, 0.975), na.rm = TRUE)

list(
  observed_mean = obs_SWmean,
  bootstrap_se = sd(boot_SWmeans, na.rm = TRUE),
  ci_95 = SWci
)

# 4. Plot bootstrap distribution
boot_SWdf <- data.frame(mean_H2 = boot_SWmeans)

pSW <- ggplot(boot_SWdf, aes(x = mean_H2)) +
  geom_histogram(bins = 40, fill = "skyblue", color = "white", alpha = 0.7) +
  geom_vline(xintercept = obs_SWmean, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = SWci, color = "darkblue", linetype = "dotted", size = 1) +
  labs(
    title = "Bootstrap distribution of mean seed width ICC (H²)",
    x = "Mean ICC (bootstrap samples)",
    y = "Frequency"
  ) +
  theme_minimal()

print(pSW)

#seed to wing area ratio
# Function to compute ICC (H2) for each provenance
get_H2 <- function(df) {
  sapply(levels(df$Provenance), function(p) {
    dsub <- subset(df, Provenance == p)
    # catch cases with too few families
    if(length(unique(dsub$Family)) < 2) return(NA)
    m <- try(lmer(SeedtoWing_Area ~ (1|Family), data = dsub), silent = TRUE)
    if(inherits(m, "try-error")) return(NA)
    vars <- as.data.frame(VarCorr(m))
    fam_var <- vars[vars$grp == "Family", "vcov"]
    res_var <- vars[vars$grp == "Residual", "vcov"]
    H2 <- (fam_var) / (fam_var + res_var)
    return(H2)
  })
}

# 1. Observed average ICC
obs_SWAH2 <- get_H2(df)
obs_SWAmean <- mean(obs_SWAH2, na.rm = TRUE)

# 2. Parallel stratified bootstrap
set.seed(123)
nboot <- 1000
ncores <- detectCores() - 1
cl <- makeCluster(ncores)

clusterExport(cl, varlist = c("df", "get_H2"), envir = environment())
clusterEvalQ(cl, library(lme4))

boot_SWAmeans <- parLapply(cl, 1:nboot, function(i) {
  # --- resample families within each provenance ---
  df_boot <- do.call(rbind, lapply(split(df, df$Provenance), function(dsub) {
    fams <- unique(dsub$Family)                                 # list of families
    sampled_fams <- sample(fams, length(fams), replace = TRUE)  # resample families with replacement
    do.call(rbind, lapply(sampled_fams, function(f) {
      dsub[dsub$Family == f, ]                                  # include all individuals from each sampled family
    }))
  }))
  
  # --- compute h2 per provenance for the bootstrap sample ---
  H2_boot <- get_H2(df_boot)
  
  # --- average across provenances ---
  mean(H2_boot, na.rm = TRUE)
})

boot_SWAmeans <- unlist(boot_SWAmeans)

# 3. CI
SWAci <- quantile(boot_SWAmeans, probs = c(0.025, 0.975), na.rm = TRUE)

list(
  observed_mean = obs_SWAmean,
  bootstrap_se = sd(boot_SWAmeans, na.rm = TRUE),
  ci_95 = SWAci
)

# 4. Plot bootstrap distribution
boot_SWAdf <- data.frame(mean_H2 = boot_SWAmeans)

pSWA <- ggplot(boot_SWAdf, aes(x = mean_H2)) +
  geom_histogram(bins = 40, fill = "skyblue", color = "white", alpha = 0.7) +
  geom_vline(xintercept = obs_SWAmean, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = SWAci, color = "darkblue", linetype = "dotted", size = 1) +
  labs(
    title = "Bootstrap distribution of mean seed to wing area ratio ICC (H²)",
    x = "Mean ICC (bootstrap samples)",
    y = "Frequency"
  ) +
  theme_minimal()

print(pSWA)

#Wing length to width ratio
# Function to compute ICC (H2) for each provenance
get_H2 <- function(df) {
  sapply(levels(df$Provenance), function(p) {
    dsub <- subset(df, Provenance == p)
    # catch cases with too few families
    if(length(unique(dsub$Family)) < 2) return(NA)
    m <- try(lmer(Wing_LengthtoWidth ~ (1|Family), data = dsub), silent = TRUE)
    if(inherits(m, "try-error")) return(NA)
    vars <- as.data.frame(VarCorr(m))
    fam_var <- vars[vars$grp == "Family", "vcov"]
    res_var <- vars[vars$grp == "Residual", "vcov"]
    H2 <- (fam_var) / (fam_var + res_var)
    return(H2)
  })
}

# 1. Observed average ICC
obs_WLWH2 <- get_H2(df)
obs_WLWmean <- mean(obs_WLWH2, na.rm = TRUE)

# 2. Parallel stratified bootstrap
set.seed(123)
nboot <- 1000
ncores <- detectCores() - 1
cl <- makeCluster(ncores)

clusterExport(cl, varlist = c("df", "get_H2"), envir = environment())
clusterEvalQ(cl, library(lme4))

boot_WLWmeans <- parLapply(cl, 1:nboot, function(i) {
  # --- resample families within each provenance ---
  df_boot <- do.call(rbind, lapply(split(df, df$Provenance), function(dsub) {
    fams <- unique(dsub$Family)                                 # list of families
    sampled_fams <- sample(fams, length(fams), replace = TRUE)  # resample families with replacement
    do.call(rbind, lapply(sampled_fams, function(f) {
      dsub[dsub$Family == f, ]                                  # include all individuals from each sampled family
    }))
  }))
  
  # --- compute h2 per provenance for the bootstrap sample ---
  H2_boot <- get_H2(df_boot)
  
  # --- average across provenances ---
  mean(H2_boot, na.rm = TRUE)
})

boot_WLWmeans <- unlist(boot_WLWmeans)

# 3. CI
WLWci <- quantile(boot_WLWmeans, probs = c(0.025, 0.975), na.rm = TRUE)

list(
  observed_mean = obs_WLWmean,
  bootstrap_se = sd(boot_WLWmeans, na.rm = TRUE),
  ci_95 = WLWci
)

# 4. Plot bootstrap distribution
boot_WLWdf <- data.frame(mean_H2 = boot_WLWmeans)

pWLW <- ggplot(boot_WLWdf, aes(x = mean_H2)) +
  geom_histogram(bins = 40, fill = "skyblue", color = "white", alpha = 0.7) +
  geom_vline(xintercept = obs_WLWmean, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = WLWci, color = "darkblue", linetype = "dotted", size = 1) +
  labs(
    title = "Bootstrap distribution of mean wing length to width ratio ICC (H²)",
    x = "Mean ICC (bootstrap samples)",
    y = "Frequency"
  ) +
  theme_minimal()

print(pWLW)

repeatability_df <- matrix(nrow = 8, ncol = 4)
rownames(repeatability_df) <- c("Wing Area", "Wing Length", "Wing Width", "Seed Area", "Seed Length", "Seed Width", "Seed to Wing Area Ratio", "Wing Length to Width Ratio")
colnames(repeatability_df) <- c("Observed_Mean", "SD", "low_CI", "high_CI")

repeatability_df[1,1] <- obs_WAmean
repeatability_df[1,2] <- sd(obs_WAH2)
repeatability_df[1,3:4] <- WAci
repeatability_df[2,1] <- obs_WLmean
repeatability_df[2,2] <- sd(obs_WLH2)
repeatability_df[2,3:4] <- WLci
repeatability_df[3,1] <- obs_WWmean
repeatability_df[3,2] <- sd(obs_WWH2)
repeatability_df[3,3:4] <- WWci
repeatability_df[4,1] <- obs_SAmean
repeatability_df[4,2] <- sd(obs_SAH2)
repeatability_df[4,3:4] <- SAci
repeatability_df[5,1] <- obs_SLmean
repeatability_df[5,2] <- sd(obs_SLH2)
repeatability_df[5,3:4] <- SLci
repeatability_df[6,1] <- obs_SWmean
repeatability_df[6,2] <- sd(obs_SWH2)
repeatability_df[6,3:4] <- SWci
repeatability_df[7,1] <- obs_SWAmean
repeatability_df[7,2] <- sd(obs_SWAH2)
repeatability_df[7,3:4] <- SWAci
repeatability_df[8,1] <- obs_WLWmean
repeatability_df[8,2] <- sd(obs_WLWH2)
repeatability_df[8,3:4] <- WLWci

repeatability_df <- as.data.frame(repeatability_df)
write.csv(repeatability_df, file = "FRANIG_SeedMorph_Repeatability_CIs.csv")

```

