---
title: "FRANIG Seed Morphology - Data Cleaning"
author: "KyraL"
date: "2025-01-13"
output: html_document
---
#Introduction
This R Notebook contains the code for cleaning and merging the data from the Fraxinus nigra seed morphology x-ray data. The data was collected in 2024 by Melissa Lehrer, Jacob Mazza, and Alex Moen. Seed and samara area, width, and length were calculated from segmented images analyzed using the centroid feature in ImageJ.

#Cleaning Data
Each person's data was imported and cleaned separately as each person followed sightly different formats for their csv files.

##MAL Data Cleaning

###Read in the data
```{r}
setwd("~/GitHub/Ash/FRANIG_Seed")
library(readxl)
library(dplyr)

#Read in all of the csv files created by MAL
file_directory <- "~/GitHub/Ash/FRANIG_Seed/Melissa"
csv_files <- list.files(file_directory, pattern = "*.csv", full.names = T)
data_list <- lapply(csv_files, function(file) {
  data <- read_csv(file)
  
  # Ensure the `Latitude` column exists and is numeric
  if ("Latitude" %in% names(data)) {
    data$Latitude <- as.numeric(data$Latitude)
  } else {
    # Add a Latitude column filled with NA if it doesn't exist
    data$Latitude <- NA
  }
  
  # Ensure the `Single_Seed_Weight` column exists and is numeric
  if ("Single_Seed_Weight" %in% names(data)) {
    data$Single_Seed_Weight <- as.numeric(data$Single_Seed_Weight)
  } else {
    # Add a Single_Seed_Weight column filled with NA if it doesn't exist
    data$Single_Seed_Weight <- NA
  }
  
  # Ensure the `SeedOrder` column exists and is numeric
  if ("SeedOrder" %in% names(data)) {
    data$SeedOrder <- as.numeric(data$SeedOrder)
  } else {
    # Add a SeedOrder column filled with NA if it doesn't exist
    data$SeedOrder <- NA
  }
  
  return(data)
})

#Combine all of the csv files into one data_frame with all columns retained
combined_data <- bind_rows(data_list)

#write the uncleaned data as a csv file for back-up purposes
write.csv(combined_data, "MergedData_Unclean_MAL.csv")
```

###Combine columns of values named different things but referring to the same measurement
The columns for each morphology trait were not consistent across all samples. For instance, some families had samara area under `Samara_Area` while others had it under `SamA`. This code combined entries from those columns into one column. Note that for MAL's data, the `Seed_Order_Combined` column refers to the number of the seed in each analyzed image, while in JM and AM's data it refers to the samara number.
```{r}
# Combine columns `Samara_Area` and `SamA` into a new column `Samara_Area_Combined`
combined_data_SamAMerged <- combined_data %>%
    mutate(Samara_Area_Combined = coalesce(Samara_Area, SamA)) %>%
  select(-Samara_Area, -SamA) # Optionally remove the original columns

# Combine columns `Samara_Length` and `SamL` into a new column `Samara_Length_Combined`
combined_data_SamLMerged <- combined_data_SamAMerged %>%
     mutate(Samara_Length_Combined = coalesce(Samara_Length, SamL)) %>%
    select(-Samara_Length, -SamL) # Optionally remove the original columns
 
# Combine columns `Samara_Width` and `SamW` into a new column `Samara_Width_Combined`
combined_data_SamWMerged <- combined_data_SamLMerged %>%
    mutate(Samara_Width_Combined = coalesce(Samara_Width, SamW)) %>%
     select(-Samara_Width, -SamW) # Optionally remove the original columns

# Combine columns `Seed_Area` , `SeA`, and `SeeA` into a new column `Seed_Area_Combined`
combined_data_SeeAMerged <- combined_data_SamWMerged %>%
     mutate(Seed_Area_Combined = coalesce(Seed_Area, SeA, SeeA)) %>%
    select(-Seed_Area, -SeA, -SeeA) # Optionally remove the original columns

# Combine columns `Seed_Length`, `SeL`, `SeeL`, and `SeX` into a new column `Seed_Length_Combined`
combined_data_SeeLMerged <- combined_data_SeeAMerged %>%
    mutate(Seed_Length_Combined = coalesce(Seed_Length, SeL, SeeL, SeX)) %>%
     select(-Seed_Length, -SeL, -SeeL, -SeX) # Optionally remove the original columns

# Combine columns `Seed_Width`, `SeW`, `SeeW`, and `SeY` into a new column `Seed_Width_Combined`
combined_data_SeeWMerged <- combined_data_SeeLMerged %>%
   mutate(Seed_Width_Combined = coalesce(Seed_Width, SeW, SeeW, SeY)) %>%
     select(-Seed_Width, -SeW, -SeeW, -SeW) # Optionally remove the original columns

# Combine columns `Seed_Number`, `SeedOrder`, `Seed_Order`, and `seedorder` into a new column `Seed_Order_Combined`
combined_data_SeedNo <- combined_data_SeeWMerged %>%
    mutate(Seed_Order_Combined = coalesce(Seed_Number, SeedOrder, Seed_Order, seedorder)) %>%
   select(-Seed_Number, -SeedOrder, -Seed_Order, -seedorder) # Optionally remove the original columns

#Remove unnecessary columns and keep only the data
combined_data_MAL_clean <- combined_data_SeedNo[,c(1,18:24)]
```

###Sanity check
Check that the data was merged correctly by comparing the raw data from the csv file with the entries in the merged dataframe.
```{r}
#FRANIG-NB-IVL-4
data_list[[1]] #data from the read-in file
combined_data_MAL_clean[combined_data_MAL_clean$Label == "FRANIG-NB-IVL-4",] #data from the merged file

```

###Swap Length & Width
In some cases, the length and width measurements for the seeds and samaras were switched during data entry or during the ImageJ analysis. Biologically, the samara and seed length should always be longer than the width. This code identifies scenarios where the width entered is larger than the length and swaps the values.
```{r}
#Switch samara length and width when width > length
combined_data_SamLWswap <- combined_data_MAL_clean %>%
  mutate(
    original_Samara_Width_Combined = Samara_Width_Combined,
    original_Samara_Length_Combined = Samara_Length_Combined,
    Samara_Width_Combined = if_else(original_Samara_Width_Combined > original_Samara_Length_Combined, original_Samara_Length_Combined, original_Samara_Width_Combined),
    Samara_Length_Combined = if_else(original_Samara_Width_Combined > original_Samara_Length_Combined, original_Samara_Width_Combined, original_Samara_Length_Combined)
  ) %>%
  select(-original_Samara_Width_Combined, -original_Samara_Length_Combined)  # Remove the temporary columns if needed

#Switch seed length and width when width > length
combined_data_SeeLWswap <- combined_data_SamLWswap %>%
  mutate(
    original_Seed_Width_Combined = Seed_Width_Combined,
    original_Seed_Length_Combined = Seed_Length_Combined,
    Seed_Width_Combined = if_else(original_Seed_Width_Combined > original_Seed_Length_Combined, original_Seed_Length_Combined, original_Seed_Width_Combined),
    Seed_Length_Combined = if_else(original_Seed_Width_Combined > original_Seed_Length_Combined, original_Seed_Width_Combined, original_Seed_Length_Combined)
  ) %>%
  select(-original_Seed_Width_Combined, -original_Seed_Length_Combined)  # Remove the temporary columns if needed
```

###final cleaning details
```{r}
#remove the .tiff suffix from the Family name
combined_data_SeeLWswap$Label <- sub("\\.tif$", "", combined_data_SeeLWswap$Label)

#rename the label column as family
colnames(combined_data_SeeLWswap)[colnames(combined_data_SeeLWswap) == "Label"] <- "Family"

#create Provenance and Seed_ID columns
combined_data_SeeLWswap$Provenance <- substr(combined_data_SeeLWswap$Family,11,13)
# Join two columns with a hyphen in the middle
combined_data_SeeLWswap$Individual_ID <- paste(combined_data_SeeLWswap$Family, combined_data_SeeLWswap$Seed_Order_Combined, sep = "-")

#rename dataframe with a logical name and save the data to a csv file
MAL_CleanSeedData_Merged <- combined_data_SeeLWswap
write.csv(MAL_CleanSeedData_Merged, file = "MergedData_Clean_MAL.csv")
```

##Clean Data JM
###Read in the data
```{r}
file_directory <- "~/GitHub/Ash/FRANIG_Seed/Jacob"
csv_files <- list.files(file_directory, pattern = "*.csv", full.names = T)
data_list <- lapply(csv_files, function(file) {
  data <- read_csv(file)
  
  #Standardize column names to lowercase
  colnames(data) <- tolower(colnames(data))
  
  #List of possible column names for seed order
  seed_order_columns <- c("seedorder", "in seed order", "seed_order")
  
  #Loop through each column name variant and handle missing or mismatched columns
  for (col in seed_order_columns) {
    if (col %in% names(data)) {
      data[[col]] <- as.numeric(data[[col]])  #Convert to numeric
    } else {
      data[[col]] <- NA  #Add the column filled with NA if the other columns are empty
    }
  }
  
  return(data)
})

#Combine all of the csv files into one data_frame with all columns retained
combined_data <- bind_rows(data_list)

#write the uncleaned data as a csv file for back-up purposes
write.csv(combined_data, file = "MergedData_Unclean_JM.csv")
```

###Remove rows with NA values
Jacob had to manually convert some measurements from pixels to mm. He kept the pixel data in the csv files so we want to remove those rows which should have NA in the 'label' column.
```{r}
#remove any rows where label = NA
combined_data_noPixelMeasurements <- combined_data %>% filter(!is.na(label))
```

###Combine columns of values named different things but referring to the same measurement

```{r}
#rename 'sama' as 'Samara_Area_Combined
colnames(combined_data_noPixelMeasurements)[colnames(combined_data_noPixelMeasurements) == "sama"] <- "Samara_Area_Combined"

#combine 'saml', 'samy...8', 'saml...8' and rename column 'Samara_Length_Combined'
combined_data_SamLMerged <- combined_data_noPixelMeasurements %>%
     mutate(Samara_Length_Combined = coalesce(saml,samy...8,saml...8)) %>%
    select(-saml, -samy, -samy...8) # Optionally remove the original columns

#combine 'samw', 'samw...7' and rename column 'Samara_Width_Combined'
combined_data_SamWMerged <- combined_data_SamLMerged %>%
    mutate(Samara_Width_Combined = coalesce(samw, samw...7)) %>%
     select(-samw, -samw...7) # Optionally remove the original columns

#combine 'seea', 'sea' and rename column 'Seed_Area_Combined'
combined_data_SeeAMerged <- combined_data_SamWMerged %>%
     mutate(Seed_Area_Combined = coalesce(seea, sea)) %>%
    select(-seea, -sea) # Optionally remove the original columns

#combine 'seel', 'sel', 'sey...14' and rename column 'Seed_Length_Combined'
combined_data_SeeLMerged <- combined_data_SeeAMerged %>%
    mutate(Seed_Length_Combined = coalesce(seel, sel, sey...14)) %>%
     select(-seel, -sel, -sey...14) # Optionally remove the original columns

#combine 'seew', 'sew' and rename column 'Seed_Width_Combined'
combined_data_SeeWMerged <- combined_data_SeeLMerged %>%
   mutate(Seed_Width_Combined = coalesce(seew, sew)) %>%
     select(-seew, -sew) # Optionally remove the original columns

#combine 'samara_order', `samara order`, '...1', `samara aorder`,`sqamara order` and rename column 'Seed_Order_Combined'
combined_data_SeedNo <- combined_data_SeeWMerged %>%
    mutate(Seed_Order_Combined = coalesce(samara_order, `samara order`, ...1, `samara aorder`,`sqamara order`)) %>%
   select(-samara_order, -`samara order`, -...1, -`samara aorder`,-`sqamara order`) # Optionally remove the original columns

#Remove unnecessary columns and keep only the data
combined_data_JM_clean <- combined_data_SeedNo[,c(2:3,10,32:37)]
```

###Sanity check
Check that the data was merged correctly by comparing the raw data from the csv file with the entries in the merged dataframe.
```{r}
#FRANIG-MN-BUF-1
data_list[[1]] #data from the read-in file
combined_data_JM_clean[combined_data_JM_clean$label == "FRANIG-MN-BUF-1.tif",] #data from the merged file

```
###Swap Length & Width
```{r}
#Swap columns where samara width is greater than samara width
combined_data_SamLWswap <- combined_data_JM_clean %>%
  mutate(
    original_Samara_Width_Combined = Samara_Width_Combined,
    original_Samara_Length_Combined = Samara_Length_Combined,
    Samara_Width_Combined = if_else(original_Samara_Width_Combined > original_Samara_Length_Combined, original_Samara_Length_Combined, original_Samara_Width_Combined),
    Samara_Length_Combined = if_else(original_Samara_Width_Combined > original_Samara_Length_Combined, original_Samara_Width_Combined, original_Samara_Length_Combined)
  ) %>%
  select(-original_Samara_Width_Combined, -original_Samara_Length_Combined)  # Remove the temporary columns if needed

#Swap columns where seed width is greater than seed length
combined_data_SeeLWswap <- combined_data_SamLWswap %>%
  mutate(
    original_Seed_Width_Combined = Seed_Width_Combined,
    original_Seed_Length_Combined = Seed_Length_Combined,
    Seed_Width_Combined = if_else(original_Seed_Width_Combined > original_Seed_Length_Combined, original_Seed_Length_Combined, original_Seed_Width_Combined),
    Seed_Length_Combined = if_else(original_Seed_Width_Combined > original_Seed_Length_Combined, original_Seed_Width_Combined, original_Seed_Length_Combined)
  ) %>%
  select(-original_Seed_Width_Combined, -original_Seed_Length_Combined)  # Remove the temporary columns if needed
```

###final cleaning details
```{r}
#remove the 'tif' suffix
combined_data_SeeLWswap$label <- sub("\\.tif$", "", combined_data_SeeLWswap$label)

#rename the label column 'Family"
colnames(combined_data_SeeLWswap)[colnames(combined_data_SeeLWswap) == "label"] <- "Family"

#make provenance and individual seed ID columns
combined_data_SeeLWswap$Provenance <- substr(combined_data_SeeLWswap$Family,11,13)
# Join two columns with a hyphen in the middle
combined_data_SeeLWswap$Individual_ID <- paste(combined_data_SeeLWswap$Family, combined_data_SeeLWswap$Seed_Order_Combined, sep = "-")

#rename dataframe with unique title and save as csv
JM_CleanSeedData_Merged <- combined_data_SeeLWswap
write.csv(JM_CleanSeedData_Merged, file = "MergedData_Clean_JM.csv")

```

##Clean Data AM
###Read in the data
```{r}
file_directory <- "~/GitHub/Ash/FRANIG_Seed/Alex"
csv_files <- list.files(file_directory, pattern = "*.csv", full.names = T)
data_list <- lapply(csv_files, function(file) {
  data <- read_csv(file)
  
  #Standardize column names to lowercase
  colnames(data) <- tolower(colnames(data))
  
  #List of possible column names for seed order
  seed_order_columns <- c("seedorder", "seed_order", "seed order")
  
  # Loop through each column name variant and handle missing or mismatched columns
  for (col in seed_order_columns) {
    if (col %in% names(data)) {
      data[[col]] <- as.numeric(data[[col]])  # Convert to numeric
    } else {
      data[[col]] <- NA  # Add the column filled with NA
    }
  }
  
  #list of columns that are present in some files but absent in others
  misc_columns <- c("sama", "saml", "...1", "x...4","y...5","samw","angle...8","label...10","seea","seew","seel")
  
  # Loop through each column name variant and handle missing or mismatched columns
  for (col in misc_columns) {
    if (col %in% names(data)) {
      data[[col]] <- as.numeric(data[[col]])  # Convert to numeric
    } else {
      data[[col]] <- NA  # Add the column filled with NA
    }
  }
  # Return the modified data frame
  return(data)
})

#combine all dataframes into one
combined_data <- bind_rows(data_list)

#save uncleaned data as csv for records
write.csv(combined_data, file = "MergedData_Unclean_AM.csv")
```

###Remove rows with NA values
```{r}
#remove rows where every entry is NA
combined_data_noNA <- combined_data %>%
  filter(!if_all(everything(), is.na))
```

###Combine columns of values named different things but referring to the same measurement
```{r}
# Combine columns 'sama', 'area...3', 'sama...3', area into a new column `Samara_Area_Combined`
combined_data_SamAMerged <- combined_data_noNA %>%
    mutate(Samara_Area_Combined = coalesce(sama, area...3, sama...3, area)) %>%
  select(-sama, -area...3, -sama...3, -area) # Optionally remove the original columns

# Combine columns 'saml', 'saml...6', 'major...6', 'major' into a new column `Samara_Length_Combined`
combined_data_SamLMerged <- combined_data_SamAMerged %>%
     mutate(Samara_Length_Combined = coalesce(saml, saml...6, major...6, major)) %>%
    select(-saml, -saml...6, -major...6, -major) # Optionally remove the original columns
 
# Combine columns 'samw', `samw+j1`, 'samw...7', 'minor...7', 'minor' into a new column `Samara_Width_Combined`
combined_data_SamWMerged <- combined_data_SamLMerged %>%
    mutate(Samara_Width_Combined = coalesce(samw, `samw+j1`, samw...7, minor...7, minor)) %>%
     select(-samw, -`samw+j1`, -samw...7, -minor...7, -minor) # Optionally remove the original columns

# Combine columns 'seea', 'area...10', 'sama...10' into a new column `Seed_Area_Combined`
combined_data_SeeAMerged <- combined_data_SamWMerged %>%
     mutate(Seed_Area_Combined = coalesce(seea, area...10,sama...10)) %>%
    select(-seea, -area...10, -sama...10) # Optionally remove the original columns

# Combine columns 'seel', 'saml...13', 'major...13' into a new column `Seed_Length_Combined`
combined_data_SeeLMerged <- combined_data_SeeAMerged %>%
    mutate(Seed_Length_Combined = coalesce(seel, saml...13, major...13)) %>%
     select(-seel, -saml...13, -major...13) # Optionally remove the original columns

# Combine columns 'seew', 'samw...14', 'minor...14' into a new column `Seed_Width_Combined`
combined_data_SeeWMerged <- combined_data_SeeLMerged %>%
   mutate(Seed_Width_Combined = coalesce(seew, samw...14, minor...14)) %>%
     select(-seew, -samw...14, -minor...14) # Optionally remove the original columns
 

# Combine columns 'samara_order', '...1' into a new column `Seed_Order_Combined`
combined_data_SeedNo <- combined_data_SeeWMerged %>%
    mutate(Seed_Order_Combined = coalesce(samara_order, ...1)) %>%
   select(-samara_order, -...1) # Optionally remove the original columns

#remove unnecessary columns
combined_data_AM_clean <- combined_data_SeedNo[,c(1,9,32:38)]
```


###Sanity check
Check that the data was merged correctly by comparing the raw data from the csv file with the entries in the merged dataframe.
```{r}
#FRANIG-IA-OTC-1
data_list[[1]] #data from the read-in file
combined_data_AM_clean[combined_data_AM_clean$label...2 == "FRANIG-IA-OTC-1.tif",] #data from the merged file
```

###Swap length & width
```{r}
#swap columns if samara width is greater than samara length
combined_data_SamLWswap <- combined_data_AM_clean %>%
  mutate(
    original_Samara_Width_Combined = Samara_Width_Combined,
    original_Samara_Length_Combined = Samara_Length_Combined,
    Samara_Width_Combined = if_else(original_Samara_Width_Combined > original_Samara_Length_Combined, original_Samara_Length_Combined, original_Samara_Width_Combined),
    Samara_Length_Combined = if_else(original_Samara_Width_Combined > original_Samara_Length_Combined, original_Samara_Width_Combined, original_Samara_Length_Combined)
  ) %>%
  select(-original_Samara_Width_Combined, -original_Samara_Length_Combined)  # Remove the temporary columns if needed

#swap columns if seed width is greater than seed length
combined_data_SeeLWswap <- combined_data_SamLWswap %>%
  mutate(
    original_Seed_Width_Combined = Seed_Width_Combined,
    original_Seed_Length_Combined = Seed_Length_Combined,
    Seed_Width_Combined = if_else(original_Seed_Width_Combined > original_Seed_Length_Combined, original_Seed_Length_Combined, original_Seed_Width_Combined),
    Seed_Length_Combined = if_else(original_Seed_Width_Combined > original_Seed_Length_Combined, original_Seed_Width_Combined, original_Seed_Length_Combined)
  ) %>%
  select(-original_Seed_Width_Combined, -original_Seed_Length_Combined)  # Remove the temporary columns if needed
```

###final cleaning details
```{r}
#remove 'tif' suffix from family names
combined_data_SeeLWswap$label...2 <- sub("\\.tif$", "", combined_data_SeeLWswap$label...2)

#rename the label column as 'Family'
colnames(combined_data_SeeLWswap)[colnames(combined_data_SeeLWswap) == "label...2"] <- "Family"

#create provenance and individual seed ID columns
combined_data_SeeLWswap$Provenance <- substr(combined_data_SeeLWswap$Family,11,13)
# Join two columns with a hyphen in the middle
combined_data_SeeLWswap$Individual_ID <- paste(combined_data_SeeLWswap$Family, combined_data_SeeLWswap$Seed_Order_Combined, sep = "-")

#rename dataframe and save data as csv file for records
AM_CleanSeedData_Merged <- combined_data_SeeLWswap
write.csv(AM_CleanSeedData_Merged, file = "MergedData_Clean_JM.csv")

```

#Merging Data

##merge dataframes
```{r}
#before merging, add a column to each person's cleaned data to make tracking down raw data easier
AM_CleanSeedData_Merged$Collector <- "AM"
MAL_CleanSeedData_Merged$Collector <- "MAL"
JM_CleanSeedData_Merged$Collector <- "JM"

#merge all data into one big data frame
all_data_merged <- bind_rows(AM_CleanSeedData_Merged, JM_CleanSeedData_Merged, MAL_CleanSeedData_Merged)
write.csv(all_data_merged, file = "AllSeedData_Merged_Unclean.csv")
```

##quality control
This code is to look for measurements that biologically don't make sense such as seed area being greater than samara area.
```{r}
#is seed area > samara area
df1 <- all_data_merged %>%
  mutate(Seed_Area_Greater = Seed_Area_Combined > Samara_Area_Combined)
df2 <- df1 %>%
  mutate(Seed_Area_Equal = Seed_Area_Combined == Samara_Area_Combined)
  #it looks like something is wrong with NB-IVL-9, we will remove the entire family as well as any other instances where the seed area is greater than the samara area
df3 <- df2 %>%
  filter(Family != "FRANIG-NB-IVL-9")
df4 <- df3 %>%
  filter(Seed_Area_Greater != "TRUE" | is.na(Seed_Area_Greater))

#is samara width > samara length
df5 <- df4 %>%
  mutate(Samara_Width_Greater = Samara_Width_Combined > Samara_Length_Combined)
#is seed width > seed length
df6 <- df5 %>%
  mutate(Seed_Width_Greater = Seed_Width_Combined > Seed_Length_Combined)
#is seed length > seed area
df7 <- df6 %>%
  mutate(Seed_Length_Area = Seed_Length_Combined > Seed_Area_Combined)
  #keeping these values for now becuase they may be real

#is seed width > seed area
df8 <- df7 %>%
  mutate(Seed_Width_Area = Seed_Width_Combined > Seed_Area_Combined)

#is samara width > samara area
df9 <- df8 %>%
  mutate(Samara_Width_Area = Samara_Width_Combined > Samara_Area_Combined)

#is samara length > samara area
df10 <- df9 %>%
  mutate(Samara_Length_Area = Samara_Length_Combined > Samara_Area_Combined)

#is seed length > samara length
df11 <- df10 %>%
  mutate(Seed_Samara_length = Seed_Length_Combined > Samara_Length_Combined)

```

##remove problematic entries
```{r}
#remove columns where seed length is greater than samara length or seed_samara_length is NA
df12 <- df11 %>%
  filter(Seed_Samara_length != "TRUE" | is.na(Seed_Samara_length))

#remove entries with no 'Family' ID
df12.1 <- df12 %>%
    filter(Family != "n/a")

#remove entries that contain only seed or samara values
df12.2 <- df12.1 %>%
  filter(!is.na(Seed_Area_Combined))

#remove entries tagged as merges/fused samaras
df12.3 <- df12.2 %>%
  filter(is.na(notes))

#remove duplicate values which are unnoted merged samaras or split seeds
df12.3$Individual_ID <- as.factor(df12.3$Individual_ID)
df12.4 <- df12.3 %>%
  group_by(Individual_ID) %>%
  filter(n() == 1) %>%
  ungroup()

#remove extraneous columns
Cleaned_SeedData <- df12.4[,c(1,3:12)]

#save cleaned and merged data to csv file
write.csv(Cleaned_SeedData, file = "AllSeedData_Merged_Clean.csv")
```