---
title: "FRANIG Seed Morphology - Trait-Trait Linear Regressions"
author: "KyraL"
date: "2026-02-12"
output: html_document
---

#Introduction
This code was used to calculate trait-trait linear regressions between greenhouse traits and seed traits averaged at the population level. We also performed a Pearson correlation between traits to see how much they covaried.

#Read in Data
```{r}
setwd("~/GitHub/Ash/FRANIG_Seed")
library(tidyverse)

#load climate and seed trait data
FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y <- read_csv("~/GitHub/Ash/FRANIG_Seed/FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y.csv")
colnames(FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y)[colnames(FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y) == "id2"] <- "Prov"

df_seedmorph <- read_csv("~/GitHub/Ash/FRANIG_Seed/df.seedmorph.csv")
df_seedmorph$`100_Seed_Weight_mg` <- as.numeric(df_seedmorph$`100_Seed_Weight_mg`)
colnames(df_seedmorph)[colnames(df_seedmorph) == "Provenance...11"] <- "Prov"

#aggregate provenance means for each trait
mean_SamA <- aggregate(Samara_Area_Combined ~ Prov, data = df_seedmorph, FUN = mean)
mean_SamW <- aggregate(Samara_Width_Combined ~ Prov, data = df_seedmorph, FUN = mean)
mean_SamL <- aggregate(Samara_Length_Combined ~ Prov, data = df_seedmorph, FUN = mean)
mean_SeeA <- aggregate(Seed_Area_Combined ~ Prov, data = df_seedmorph, FUN = mean)
mean_SeeW <- aggregate(Seed_Width_Combined ~ Prov, data = df_seedmorph, FUN = mean)
mean_SeeL <- aggregate(Seed_Length_Combined ~ Prov, data = df_seedmorph, FUN = mean)
mean_SeeSamA <- aggregate(Seed_Samara_AreaRatio ~ Prov, data = df_seedmorph, FUN = mean)
mean_SamWL <- aggregate(Samara_WidthLengthRatio ~ Prov, data = df_seedmorph, FUN = mean)
mean_SW <- aggregate(`100_Seed_Weight_mg` ~ Prov, data = df_seedmorph, FUN = mean)
df_list <- list(mean_SamA, mean_SamL, mean_SamW, mean_SeeA, mean_SeeL, mean_SeeW, mean_SeeSamA, mean_SamWL, mean_SW)
morphological_trait_populationmeans <- reduce(df_list, full_join, by = "Prov")

#merge climate and seed trait data
climate_morphology_merged <- left_join(morphological_trait_populationmeans, FRANIGSeedMorph_PopulationCentroide_NoYearStrat_Normal_1961_1990Y, by = "Prov")
climate_morphology_merged <- climate_morphology_merged[!is.na(climate_morphology_merged$Latitude),]

#add in greenhouse traits
FRANIG_HC_MORPH_COMPLETE <- read_csv("~/GitHub/Ash/FRANIG_Seed/FRANIG_HC_MORPH_COMPLETE.csv")
greenhouse_traits <- FRANIG_HC_MORPH_COMPLETE[,c(3,7,9:12,20)]
colnames(greenhouse_traits)[colnames(greenhouse_traits) == "id2"] <- "Prov"

#calculate population means
mean_propemerged <- aggregate(Proportion_Emerged ~ Prov, data = greenhouse_traits, FUN = mean)
mean_height <- aggregate(Height_cm ~ Prov, data = greenhouse_traits, FUN = mean)
mean_emergencetime <- aggregate(Time_to_Emergence ~ Prov, data = greenhouse_traits, FUN = mean)
mean_trueleaftime<- aggregate(Time_to_TrueLeaves ~ Prov, data = greenhouse_traits, FUN = mean)
mean_compoundleaftime <- aggregate(Time_to_CompoundLeaves ~ Prov, data = greenhouse_traits, FUN = mean)
df_list <- list(mean_propemerged, mean_height, mean_emergencetime, mean_trueleaftime, mean_compoundleaftime)
greenhouse_trait_populationmeans <- reduce(df_list, full_join, by = "Prov")

#merge seed traits, greenhouse traits, and climate data
climate_morphology_merged <- left_join(climate_morphology_merged, greenhouse_trait_populationmeans, by = "Prov")

colnames(climate_morphology_merged) <- c("Prov", "Wing_Area","Wing_Length","Wing_Width","Seed_Area", "Seed_Length","Seed_Width","Seed_to_Wing_AreaRatio","Wing_Length_to_WidthRatio","Seed_Weight",
"id1", "Latitude", "Longitude","Elevation", "MAT", "MWMT", "MCMT" ,"TD", "MAP", "MSP", "AHM" ,"SHM" , "DD_0", "DD5" ,"DD_18" ,"DD18", "NFFD",  "bFFP","eFFP" , "FFP", "PAS" , "EMT",  "EXT"  ,"MAR" ,"Eref" , "CMD", "RH", "CMI" ,"DD1040", "Proportion_Emerged", "Height_cm" ,"Time_to_Emergence" ,"Time_to_TrueLeaves", "Time_to_CompoundLeaves")

```

#trait-trait correlations
```{r}
#subset trait data
traits <- climate_morphology_merged[,c(2:10,40:44,47)]

cor_matrix<-cor(traits, method = "pearson" ,
                  use = "pairwise.complete.obs")
library(corrplot)
corrplot(cor_matrix, method = "color", type = "lower", col = colorRampPalette(c("blue", "white", "red"))(200),addCoef.col = "black", tl.cex = 0.8,tl.col = "black", number.cex = 0.4)
```

#Linear regressions
##Proportion Emerged
```{r}
library(cowplot)
library(gridExtra)
#proportion emerged
y_var <- "Proportion_Emerged"
x_vars <- c("Seed_Weight", "Wing_Area", "Seed_Area", "Wing_Length","Seed_Length","Wing_Width","Seed_Width", "Seed_to_Wing_AreaRatio", "Wing_Length_to_WidthRatio")

plot_list <- list()
model_list <- list()

for (x_var in x_vars) {
  
  # Fit the linear model
  formula <- as.formula(paste(y_var, "~", x_var))  # Create formula dynamically
  model <- lm(formula, data = climate_morphology_merged)
  
  model_list[[x_var]] <- model
  
  # Extract R² and p-value
  r2 <- summary(model)$r.squared
  p_value <- summary(model)$coefficients[2, 4]
  
   # Determine top-right position dynamically
  x_pos <- max(climate_morphology_merged[[x_var]], na.rm = TRUE) * 0.9  # Slightly left from max x
  y_pos <- max(climate_morphology_merged[[y_var]], na.rm = TRUE) * 0.9  # Slightly below max y
  
  # Generate ggplot
  p <- ggplot(climate_morphology_merged, aes_string(x = x_var, y = y_var)) +  # Use aes_string() for dynamic mapping
    geom_point() + 
    geom_smooth(method = "lm", se = T, color = "blue") +
    annotate("text", x = x_pos, y = y_pos,
             label = paste0("R² = ", round(r2, 3), "\nP = ", signif(p_value, 3)),
             size = 3, color = "black") + theme(panel.background = element_blank(), panel.grid.major =    element_line("grey")) +
    ggtitle(paste("Proportion Emerged", "vs", x_var)) + ylab("Proportion Emerged")
  
  # Print each plot
  plot_list[[x_var]] <- p
}

library(purrr)
library(dplyr)

model_summary <- map_dfr(
  model_list,
  ~{
    sm <- summary(.x)
    coefs <- sm$coefficients
    
    tibble(
      R_squared = sm$r.squared,
      Estimate  = coefs[2, "Estimate"],
      Std_Error = coefs[2, "Std. Error"],
      P_value   = coefs[2, "Pr(>|t|)"]
    )
  },
  .id = "Predictor"
)
write.csv(model_summary, file = "Proportion_emerged_SeedMoprh_Stats_PopLevel.csv")

plots_combined <- marrangeGrob(grobs = plot_list, ncol = 2, nrow = 3)

ggsave("Proportion Emerged_SeedMorphRegressions_PopLevel.pdf", plots_combined, width = 10, height = 7)


# Create a list to store diagnostic plots
diagnostic_plots <- list()

# Loop through each model in model_list
for (x_var in names(model_list)) {
  
  model <- model_list[[x_var]]
  resid <- residuals(model)
  fitted <- fitted(model)
  
  # --- QQ Plot of residuals ---
  qq_data <- data.frame(
    Theoretical = qqnorm(resid, plot.it = FALSE)$x,
    Sample = qqnorm(resid, plot.it = FALSE)$y
  )
  
  # Compute slope and intercept for qqline (like base R qqline)
  q_theoretical <- quantile(qq_data$Theoretical, probs = c(0.25, 0.75))
  q_sample <- quantile(qq_data$Sample, probs = c(0.25, 0.75))
  slope <- diff(q_sample) / diff(q_theoretical)
  intercept <- q_sample[1] - slope * q_theoretical[1]
  
  # --- QQ Plot with QQ Line ---
  qq_plot <- ggplot(qq_data, aes(x = Theoretical, y = Sample)) +
    geom_point() +
    geom_abline(slope = slope, intercept = intercept, color = "red", linetype = "dashed", linewidth = 0.8) +
    ggtitle(paste("QQ Plot of Residuals for", x_var)) +
    theme_bw()
  
  # --- Residuals vs Fitted Plot ---
  resid_plot <- ggplot(data.frame(Fitted = fitted, Residuals = resid),
                       aes(x = Fitted, y = Residuals)) +
    geom_point() +
    geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
    ggtitle(paste("Residuals vs Fitted for", x_var)) +
    xlab("Fitted Values") +
    ylab("Residuals") +
    theme_bw()
  
  # Combine both plots vertically
  combined_plot <- gridExtra::grid.arrange(qq_plot, resid_plot, ncol = 1)
  
  diagnostic_plots[[x_var]] <- combined_plot
}

# Save all diagnostic plots to a single PDF

plots_combined <- marrangeGrob(grobs = diagnostic_plots, ncol = 2, nrow = 2)

ggsave("Proportion Emerged_SeedMorph_Diagnostics_PopLevel.pdf", plots_combined, width = 10, height = 7)

```
##Height
```{r}
library(cowplot)
library(gridExtra)
#proportion emerged
y_var <- "Height_cm"
x_vars <- c("Seed_Weight", "Wing_Area", "Seed_Area", "Wing_Length","Seed_Length","Wing_Width","Seed_Width", "Seed_to_Wing_AreaRatio", "Wing_Length_to_WidthRatio")

plot_list <- list()
model_list <- list()

for (x_var in x_vars) {
  
  # Fit the linear model
  formula <- as.formula(paste(y_var, "~", x_var))  # Create formula dynamically
  model <- lm(formula, data = climate_morphology_merged)
  
  model_list[[x_var]] <- model
  
  # Extract R² and p-value
  r2 <- summary(model)$r.squared
  p_value <- summary(model)$coefficients[2, 4]
  
   # Determine top-right position dynamically
  x_pos <- max(climate_morphology_merged[[x_var]], na.rm = TRUE) * 0.9  # Slightly left from max x
  y_pos <- max(climate_morphology_merged[[y_var]], na.rm = TRUE) * 0.9  # Slightly below max y
  
  # Generate ggplot
  p <- ggplot(climate_morphology_merged, aes_string(x = x_var, y = y_var)) +  # Use aes_string() for dynamic mapping
    geom_point() + 
    geom_smooth(method = "lm", se = T, color = "blue") +
    annotate("text", x = x_pos, y = y_pos,
             label = paste0("R² = ", round(r2, 3), "\nP = ", signif(p_value, 3)),
             size = 3, color = "black") + theme(panel.background = element_blank(), panel.grid.major =    element_line("grey")) +
    ggtitle(paste("Height", "vs", x_var)) + ylab("Height")
  
  # Print each plot
  plot_list[[x_var]] <- p
}

library(purrr)
library(dplyr)

model_summary <- map_dfr(
  model_list,
  ~{
    sm <- summary(.x)
    coefs <- sm$coefficients
    
    tibble(
      R_squared = sm$r.squared,
      Estimate  = coefs[2, "Estimate"],
      Std_Error = coefs[2, "Std. Error"],
      P_value   = coefs[2, "Pr(>|t|)"]
    )
  },
  .id = "Predictor"
)
write.csv(model_summary, file = "Height_SeedMoprh_Stats_PopLevel.csv")

plots_combined <- marrangeGrob(grobs = plot_list, ncol = 2, nrow = 3)

ggsave("Height_SeedMorphRegressions_PopLevel.pdf", plots_combined, width = 10, height = 7)


# Create a list to store diagnostic plots
diagnostic_plots <- list()

# Loop through each model in model_list
for (x_var in names(model_list)) {
  
  model <- model_list[[x_var]]
  resid <- residuals(model)
  fitted <- fitted(model)
  
  # --- QQ Plot of residuals ---
  qq_data <- data.frame(
    Theoretical = qqnorm(resid, plot.it = FALSE)$x,
    Sample = qqnorm(resid, plot.it = FALSE)$y
  )
  
  # Compute slope and intercept for qqline (like base R qqline)
  q_theoretical <- quantile(qq_data$Theoretical, probs = c(0.25, 0.75))
  q_sample <- quantile(qq_data$Sample, probs = c(0.25, 0.75))
  slope <- diff(q_sample) / diff(q_theoretical)
  intercept <- q_sample[1] - slope * q_theoretical[1]
  
  # --- QQ Plot with QQ Line ---
  qq_plot <- ggplot(qq_data, aes(x = Theoretical, y = Sample)) +
    geom_point() +
    geom_abline(slope = slope, intercept = intercept, color = "red", linetype = "dashed", linewidth = 0.8) +
    ggtitle(paste("QQ Plot of Residuals for", x_var)) +
    theme_bw()
  
  # --- Residuals vs Fitted Plot ---
  resid_plot <- ggplot(data.frame(Fitted = fitted, Residuals = resid),
                       aes(x = Fitted, y = Residuals)) +
    geom_point() +
    geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
    ggtitle(paste("Residuals vs Fitted for", x_var)) +
    xlab("Fitted Values") +
    ylab("Residuals") +
    theme_bw()
  
  # Combine both plots vertically
  combined_plot <- gridExtra::grid.arrange(qq_plot, resid_plot, ncol = 1)
  
  diagnostic_plots[[x_var]] <- combined_plot
}

# Save all diagnostic plots to a single PDF

plots_combined <- marrangeGrob(grobs = diagnostic_plots, ncol = 2, nrow = 2)

ggsave("Height_SeedMorph_Diagnostics_PopLevel.pdf", plots_combined, width = 10, height = 7)

```
##Time to Emergence
```{r}
library(cowplot)
library(gridExtra)
#proportion emerged
y_var <- "Time_to_Emergence"
x_vars <- c("Seed_Weight", "Wing_Area", "Seed_Area", "Wing_Length","Seed_Length","Wing_Width","Seed_Width", "Seed_to_Wing_AreaRatio", "Wing_Length_to_WidthRatio")

plot_list <- list()
model_list <- list()

for (x_var in x_vars) {
  
  # Fit the linear model
  formula <- as.formula(paste(y_var, "~", x_var))  # Create formula dynamically
  model <- lm(formula, data = climate_morphology_merged)
  
  model_list[[x_var]] <- model
  
  # Extract R² and p-value
  r2 <- summary(model)$r.squared
  p_value <- summary(model)$coefficients[2, 4]
  
   # Determine top-right position dynamically
  x_pos <- max(climate_morphology_merged[[x_var]], na.rm = TRUE) * 0.9  # Slightly left from max x
  y_pos <- max(climate_morphology_merged[[y_var]], na.rm = TRUE) * 0.9  # Slightly below max y
  
  # Generate ggplot
  p <- ggplot(climate_morphology_merged, aes_string(x = x_var, y = y_var)) +  # Use aes_string() for dynamic mapping
    geom_point() + 
    geom_smooth(method = "lm", se = T, color = "blue") +
    annotate("text", x = x_pos, y = y_pos,
             label = paste0("R² = ", round(r2, 3), "\nP = ", signif(p_value, 3)),
             size = 3, color = "black") + theme(panel.background = element_blank(), panel.grid.major =    element_line("grey")) +
    ggtitle(paste("Time to Emergence", "vs", x_var)) + ylab("Time to Emergence")
  
  # Print each plot
  plot_list[[x_var]] <- p
}

library(purrr)
library(dplyr)

model_summary <- map_dfr(
  model_list,
  ~{
    sm <- summary(.x)
    coefs <- sm$coefficients
    
    tibble(
      R_squared = sm$r.squared,
      Estimate  = coefs[2, "Estimate"],
      Std_Error = coefs[2, "Std. Error"],
      P_value   = coefs[2, "Pr(>|t|)"]
    )
  },
  .id = "Predictor"
)
write.csv(model_summary, file = "Time_to_Emergence_SeedMoprh_Stats_PopLevel.csv")

plots_combined <- marrangeGrob(grobs = plot_list, ncol = 2, nrow = 3)

ggsave("Time_to_Emergence_SeedMorphRegressions_PopLevel.pdf", plots_combined, width = 10, height = 7)


# Create a list to store diagnostic plots
diagnostic_plots <- list()

# Loop through each model in model_list
for (x_var in names(model_list)) {
  
  model <- model_list[[x_var]]
  resid <- residuals(model)
  fitted <- fitted(model)
  
  # --- QQ Plot of residuals ---
  qq_data <- data.frame(
    Theoretical = qqnorm(resid, plot.it = FALSE)$x,
    Sample = qqnorm(resid, plot.it = FALSE)$y
  )
  
  # Compute slope and intercept for qqline (like base R qqline)
  q_theoretical <- quantile(qq_data$Theoretical, probs = c(0.25, 0.75))
  q_sample <- quantile(qq_data$Sample, probs = c(0.25, 0.75))
  slope <- diff(q_sample) / diff(q_theoretical)
  intercept <- q_sample[1] - slope * q_theoretical[1]
  
  # --- QQ Plot with QQ Line ---
  qq_plot <- ggplot(qq_data, aes(x = Theoretical, y = Sample)) +
    geom_point() +
    geom_abline(slope = slope, intercept = intercept, color = "red", linetype = "dashed", linewidth = 0.8) +
    ggtitle(paste("QQ Plot of Residuals for", x_var)) +
    theme_bw()
  
  # --- Residuals vs Fitted Plot ---
  resid_plot <- ggplot(data.frame(Fitted = fitted, Residuals = resid),
                       aes(x = Fitted, y = Residuals)) +
    geom_point() +
    geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
    ggtitle(paste("Residuals vs Fitted for", x_var)) +
    xlab("Fitted Values") +
    ylab("Residuals") +
    theme_bw()
  
  # Combine both plots vertically
  combined_plot <- gridExtra::grid.arrange(qq_plot, resid_plot, ncol = 1)
  
  diagnostic_plots[[x_var]] <- combined_plot
}

# Save all diagnostic plots to a single PDF

plots_combined <- marrangeGrob(grobs = diagnostic_plots, ncol = 2, nrow = 2)

ggsave("Time_to_Emergence_SeedMorph_Diagnostics_PopLevel.pdf", plots_combined, width = 10, height = 7)

```
##Time to True Leaves
```{r}
library(cowplot)
library(gridExtra)
#proportion emerged
y_var <- "Time_to_TrueLeaves"
x_vars <- c("Seed_Weight", "Wing_Area", "Seed_Area", "Wing_Length","Seed_Length","Wing_Width","Seed_Width", "Seed_to_Wing_AreaRatio", "Wing_Length_to_WidthRatio")

plot_list <- list()
model_list <- list()

for (x_var in x_vars) {
  
  # Fit the linear model
  formula <- as.formula(paste(y_var, "~", x_var))  # Create formula dynamically
  model <- lm(formula, data = climate_morphology_merged)
  
  model_list[[x_var]] <- model
  
  # Extract R² and p-value
  r2 <- summary(model)$r.squared
  p_value <- summary(model)$coefficients[2, 4]
  
   # Determine top-right position dynamically
  x_pos <- max(climate_morphology_merged[[x_var]], na.rm = TRUE) * 0.9  # Slightly left from max x
  y_pos <- max(climate_morphology_merged[[y_var]], na.rm = TRUE) * 0.9  # Slightly below max y
  
  # Generate ggplot
  p <- ggplot(climate_morphology_merged, aes_string(x = x_var, y = y_var)) +  # Use aes_string() for dynamic mapping
    geom_point() + 
    geom_smooth(method = "lm", se = T, color = "blue") +
    annotate("text", x = x_pos, y = y_pos,
             label = paste0("R² = ", round(r2, 3), "\nP = ", signif(p_value, 3)),
             size = 3, color = "black") + theme(panel.background = element_blank(), panel.grid.major =    element_line("grey")) +
    ggtitle(paste("Time to True Leaves", "vs", x_var)) + ylab("Time to True Leaves")
  
  # Print each plot
  plot_list[[x_var]] <- p
}

library(purrr)
library(dplyr)

model_summary <- map_dfr(
  model_list,
  ~{
    sm <- summary(.x)
    coefs <- sm$coefficients
    
    tibble(
      R_squared = sm$r.squared,
      Estimate  = coefs[2, "Estimate"],
      Std_Error = coefs[2, "Std. Error"],
      P_value   = coefs[2, "Pr(>|t|)"]
    )
  },
  .id = "Predictor"
)
write.csv(model_summary, file = "Time_to_TrueLeaves_SeedMoprh_Stats_PopLevel.csv")

plots_combined <- marrangeGrob(grobs = plot_list, ncol = 2, nrow = 3)

ggsave("Time_to_TrueLeaves_SeedMorphRegressions_PopLevel.pdf", plots_combined, width = 10, height = 7)


# Create a list to store diagnostic plots
diagnostic_plots <- list()

# Loop through each model in model_list
for (x_var in names(model_list)) {
  
  model <- model_list[[x_var]]
  resid <- residuals(model)
  fitted <- fitted(model)
  
  # --- QQ Plot of residuals ---
  qq_data <- data.frame(
    Theoretical = qqnorm(resid, plot.it = FALSE)$x,
    Sample = qqnorm(resid, plot.it = FALSE)$y
  )
  
  # Compute slope and intercept for qqline (like base R qqline)
  q_theoretical <- quantile(qq_data$Theoretical, probs = c(0.25, 0.75))
  q_sample <- quantile(qq_data$Sample, probs = c(0.25, 0.75))
  slope <- diff(q_sample) / diff(q_theoretical)
  intercept <- q_sample[1] - slope * q_theoretical[1]
  
  # --- QQ Plot with QQ Line ---
  qq_plot <- ggplot(qq_data, aes(x = Theoretical, y = Sample)) +
    geom_point() +
    geom_abline(slope = slope, intercept = intercept, color = "red", linetype = "dashed", linewidth = 0.8) +
    ggtitle(paste("QQ Plot of Residuals for", x_var)) +
    theme_bw()
  
  # --- Residuals vs Fitted Plot ---
  resid_plot <- ggplot(data.frame(Fitted = fitted, Residuals = resid),
                       aes(x = Fitted, y = Residuals)) +
    geom_point() +
    geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
    ggtitle(paste("Residuals vs Fitted for", x_var)) +
    xlab("Fitted Values") +
    ylab("Residuals") +
    theme_bw()
  
  # Combine both plots vertically
  combined_plot <- gridExtra::grid.arrange(qq_plot, resid_plot, ncol = 1)
  
  diagnostic_plots[[x_var]] <- combined_plot
}

# Save all diagnostic plots to a single PDF

plots_combined <- marrangeGrob(grobs = diagnostic_plots, ncol = 2, nrow = 2)

ggsave("Time_to_TrueLeaves_SeedMorph_Diagnostics_PopLevel.pdf", plots_combined, width = 10, height = 7)

```
##Time to Compound Leaves
```{r}
library(cowplot)
library(gridExtra)
#proportion emerged
y_var <- "Time_to_CompoundLeaves"
x_vars <- c("Seed_Weight", "Wing_Area", "Seed_Area", "Wing_Length","Seed_Length","Wing_Width","Seed_Width", "Seed_to_Wing_AreaRatio", "Wing_Length_to_WidthRatio")

plot_list <- list()
model_list <- list()

for (x_var in x_vars) {
  
  # Fit the linear model
  formula <- as.formula(paste(y_var, "~", x_var))  # Create formula dynamically
  model <- lm(formula, data = climate_morphology_merged)
  
  model_list[[x_var]] <- model
  
  # Extract R² and p-value
  r2 <- summary(model)$r.squared
  p_value <- summary(model)$coefficients[2, 4]
  
   # Determine top-right position dynamically
  x_pos <- max(climate_morphology_merged[[x_var]], na.rm = TRUE) * 0.9  # Slightly left from max x
  y_pos <- max(climate_morphology_merged[[y_var]], na.rm = TRUE) * 0.9  # Slightly below max y
  
  # Generate ggplot
  p <- ggplot(climate_morphology_merged, aes_string(x = x_var, y = y_var)) +  # Use aes_string() for dynamic mapping
    geom_point() + 
    geom_smooth(method = "lm", se = T, color = "blue") +
    annotate("text", x = x_pos, y = y_pos,
             label = paste0("R² = ", round(r2, 3), "\nP = ", signif(p_value, 3)),
             size = 3, color = "black") + theme(panel.background = element_blank(), panel.grid.major =    element_line("grey")) +
    ggtitle(paste("Time to Compound Leaves", "vs", x_var)) + ylab("Time to Compound Leaves")
  
  # Print each plot
  plot_list[[x_var]] <- p
}

library(purrr)
library(dplyr)

model_summary <- map_dfr(
  model_list,
  ~{
    sm <- summary(.x)
    coefs <- sm$coefficients
    
    tibble(
      R_squared = sm$r.squared,
      Estimate  = coefs[2, "Estimate"],
      Std_Error = coefs[2, "Std. Error"],
      P_value   = coefs[2, "Pr(>|t|)"]
    )
  },
  .id = "Predictor"
)
write.csv(model_summary, file = "Time_to_CompLeaves_SeedMoprh_Stats_PopLevel.csv")

plots_combined <- marrangeGrob(grobs = plot_list, ncol = 2, nrow = 3)

ggsave("Time_to_CompLeaves_SeedMorphRegressions_PopLevel.pdf", plots_combined, width = 10, height = 7)


# Create a list to store diagnostic plots
diagnostic_plots <- list()

# Loop through each model in model_list
for (x_var in names(model_list)) {
  
  model <- model_list[[x_var]]
  resid <- residuals(model)
  fitted <- fitted(model)
  
  # --- QQ Plot of residuals ---
  qq_data <- data.frame(
    Theoretical = qqnorm(resid, plot.it = FALSE)$x,
    Sample = qqnorm(resid, plot.it = FALSE)$y
  )
  
  # Compute slope and intercept for qqline (like base R qqline)
  q_theoretical <- quantile(qq_data$Theoretical, probs = c(0.25, 0.75))
  q_sample <- quantile(qq_data$Sample, probs = c(0.25, 0.75))
  slope <- diff(q_sample) / diff(q_theoretical)
  intercept <- q_sample[1] - slope * q_theoretical[1]
  
  # --- QQ Plot with QQ Line ---
  qq_plot <- ggplot(qq_data, aes(x = Theoretical, y = Sample)) +
    geom_point() +
    geom_abline(slope = slope, intercept = intercept, color = "red", linetype = "dashed", linewidth = 0.8) +
    ggtitle(paste("QQ Plot of Residuals for", x_var)) +
    theme_bw()
  
  # --- Residuals vs Fitted Plot ---
  resid_plot <- ggplot(data.frame(Fitted = fitted, Residuals = resid),
                       aes(x = Fitted, y = Residuals)) +
    geom_point() +
    geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
    ggtitle(paste("Residuals vs Fitted for", x_var)) +
    xlab("Fitted Values") +
    ylab("Residuals") +
    theme_bw()
  
  # Combine both plots vertically
  combined_plot <- gridExtra::grid.arrange(qq_plot, resid_plot, ncol = 1)
  
  diagnostic_plots[[x_var]] <- combined_plot
}

# Save all diagnostic plots to a single PDF

plots_combined <- marrangeGrob(grobs = diagnostic_plots, ncol = 2, nrow = 2)

ggsave("Time_to_CompLeaves_SeedMorph_Diagnostics_PopLevel.pdf", plots_combined, width = 10, height = 7)

```

#manuscript plot
```{r}
a <- ggplot(climate_morphology_merged, aes(x = Seed_Weight, y = Proportion_Emerged)) +
    geom_point()+theme(panel.background = element_blank(), panel.grid.major =    element_line("grey"), panel.border = element_rect(color = "black", fill = NA)) +
    theme(axis.text.x = element_text(angle = 0, hjust = 1)) +
    labs(y = "Proportion Emerged", x = "Seed Mass (mg)") + geom_smooth(method = "lm", se = T)
b <- ggplot(climate_morphology_merged, aes(x = Seed_Weight, y = Height_cm)) +
    geom_point()+theme(panel.background = element_blank(), panel.grid.major =    element_line("grey"), panel.border = element_rect(color = "black", fill = NA)) +
    theme(axis.text.x = element_text(angle = 0, hjust = 1)) +
    labs(y = "Height (cm)", x = "Seed Mass (mg)") + geom_smooth(method = "lm", se = T)
c <- ggplot(climate_morphology_merged, aes(x = Seed_Weight, y = Time_to_TrueLeaves)) +
    geom_point()+theme(panel.background = element_blank(), panel.grid.major =    element_line("grey"), panel.border = element_rect(color = "black", fill = NA)) +
    theme(axis.text.x = element_text(angle = 0, hjust = 1)) +
    labs(y = "Time to True Leaves (days)", x = "Seed Mass (mg)") + geom_smooth(method = "lm", se = T)

plot <- plot_grid(a,c,b, labels = c("A","B","C"), ncol = 3, nrow = 2, align = "h")

modelA <- lm(Proportion_Emerged~Seed_Weight, data = climate_morphology_merged)
summary(modelA)
modelB <- lm(Time_to_TrueLeaves~Seed_Weight, data = climate_morphology_merged)
summary(modelB)
modelC <- lm(Height_cm~Seed_Weight, data = climate_morphology_merged)
summary(modelC)

```

